---
title: Marker Genes
jupyter:
  jupytext:
    formats: 'ipynb,qmd:quarto'
    text_representation:
      extension: .qmd
      format_name: quarto
      format_version: '1.0'
      jupytext_version: 1.16.1
  kernelspec:
    display_name: R 4.4.1
    language: R
    name: ir441
---

# Setup

```{r}
# Working directory should be the root directory of repository.
# setwd("./")
renv::load()
source("./results/utils.R")

suppressPackageStartupMessages({
  library(CAdir)
  library(APL)

  library(SingleCellExperiment)
  library(scater)
  library(scuttle)
  library(scran)

  library(dplyr)
  library(tidyr)
  library(ggsankey)
  # library(legendry)
  library(patchwork)
})

options(repr.plot.width = 20, repr.plot.height = 15)
set.seed(2358)
dir <- "./results/"
imgdir <- file.path(dir, "img/review/marker_genes/")
dir.create(imgdir, recursive = TRUE)
```



## Load data

```{r}
options(future.globals.maxSize = 850 * 1024^2)
sce_org <- sce_pbmc3k()
```

# CAdir

```{r}
set.seed(1234)

sce <- sce_org
sce_var <- scran::modelGeneVar(sce)
sce_top <- scran::getTopHVGs(sce_var, n = 1000, var.threshold = NULL) #1000
sce <- sce[sce_top, ]

ca <- cacomp(
  obj = as.matrix(logcounts(sce)),
  princ_coords = 3,
  dims = 20, #20
  top = nrow(sce),
  residuals = "pearson",
  clip = TRUE
)
```

## Split & Merge Clustering

```{r}

set.seed(8) #8
cabic <- dirclust_splitmerge(
  caobj = ca,
  k = 7, #7
  cutoff = 50, #50
  method = "random",
  apl_quant = 0.999,
  min_cells = 15,
  apl_cutoff_reps = 100,
  qcutoff = 0.30, #0.4
  convergence_thr = 0.001
)

cabic <- CAdir::annotate_biclusters(
  obj = cabic,
  universe = rownames(sce),
  org = "hs"
)

cabic <- rank_genes(cadir = cabic, caobj = ca)
cabic

topg <- top_genes(cabic)

sce$cadir <- cabic@cell_clusters
ari <- aricode::clustComp(sce$cadir, sce$cell_type)
cat("\nARI:", ari$ARI, "\n")
```

### Annotate clusters

```{r}
sce <- runUMAP(sce, ntop = 2000)
um1 <- plotUMAP(sce, colour = "cadir")
um2 <- plotUMAP(sce, colour = "cell_type")

p <- um1 + ggtitle(paste0("ARI: ", round(ari$ARI, 2))) + um2
# p

ggsave(
  plot = p,
  file = file.path(imgdir, "umap.png"),
  width = 3600,
  height = 1800,
  units = "px"
)
```

# Plot clusters

```{r}
b_cells <- cluster_apl(
  ca,
  cabic,
  cluster = "B_cell",
  direction = cabic@directions["B_cell", ],
  group = which(cabic@cell_clusters == "B_cell"),
  highlight_cluster = TRUE,
  show_genes = TRUE,
  label_genes = TRUE,
  show_lines = FALSE,
  size_factor = 0.5,
  ntop = 10
)

ggsave(
  plot = b_cells,
  file = file.path(imgdir, "b_cells_apl.pdf"),
  width = 1600,
  height = 1600,
  units = "px"
)
```

## Sankey of clustering
```{r}

sce_sank <- sce

data <- colData(sce_sank) %>%
  as.data.frame() %>%
  rename("CAdir" = "cadir", "Annotation" = "cell_type")

df <- data %>%
  make_long(CAdir, Annotation)

info <- data.frame(
  Biclusters = as.factor(data$CAdir),
  Truth = as.character(data$Annotation)
) %>%
  as_tibble() %>%
  group_by(Biclusters, Truth) %>%
  summarise(n = n()) %>%
  group_by(Truth) %>%
  mutate(Partition = n / sum(n)) %>%
  ungroup() %>%
  as.data.frame() %>%
  group_by(Truth) %>%
  filter(Partition == max(Partition)) %>%
  dplyr::select(Biclusters, Truth) %>%
  distinct(Biclusters, .keep_all = TRUE)

# pal <- mpi_extend_pal()
# cols <- pal(length(unique(sce_sank$cadir)))

save_cols <- c(
  "#006c66", # MPG-CD-Grün
  "#c6d325", # MPG Hellgrün
  "#ef7c00", # MPG Orange
  # "#29485d", # MPG Dunkelblau
  "#00b1ea", # MPG Hellblau
  "#777777", # MPG-Dunkelgrau
  "#d44a3d", # Warm Red
  "#8c5fa8", # Soft Purple
  "#a7a7a8", # MPG-Grau
  "#f4c542", # Golden Yellow
  "#d95276", # Rich Pink
  "#a25b43", # Warm Brown
  "#00CED1" # Soft Cyan
)

cols <- save_cols[seq_len(length(unique(sce_sank$cadir)))]
names(cols) <- unique(sce_sank$cadir)

info <- left_join(
  data.frame("Biclusters" = names(cols), "col" = cols),
  info,
  by = "Biclusters"
)

cols <- c(cols, info$col)

names(cols) <- c(as.character(unique(sce_sank$cadir)), info$Truth)

order <- c(
  "Naive_CD4+_T_cell",
  "Monocyte",
  "Dendritic_cell",
  "CD8+_T_cell",
  "Cytotoxic_CD4+_T_cell",
  "B_cell",
  "Megakaryocyte",
  "0 - Naive CD4 T",
  "2 - Memory CD4 T",
  "1 - CD14+ Mono",
  "5 - FCGR3A+ Mono",
  "7 - DC",
  "4 - CD8 T",
  "6 - NK",
  "3 - B",
  "8 - Platelet"
)

df$node <- gsub("_", " ", df$node)
df$next_node <- gsub("_", " ", df$next_node)
names(cols) <- gsub("_", " ", names(cols))
order <- gsub("_", " ", order)

wrap <- 17
df$node <- factor(
  stringr::str_wrap(df$node, wrap),
  levels = stringr::str_wrap(order, wrap)
)
df$next_node <- factor(
  stringr::str_wrap(df$next_node, wrap),
  levels = stringr::str_wrap(order, wrap)
)

names(cols) <- stringr::str_wrap(names(cols), wrap)

sank <- ggplot(
  df,
  aes(
    x = x,
    next_x = next_x,
    node = node,
    next_node = next_node,
    fill = node,
    label = as.character(node)
  )
) +
  geom_sankey(
    flow.alpha = 0.4,
  ) +
  geom_sankey_label(size = 6) +
  labs(x = "") +
  scale_fill_manual(values = cols) +
  theme_sankey(base_size = 26, base_family = "sans") +
  theme(
    legend.position = "none"
  )

sank4panel <- ggplot(
  df,
  aes(
    x = x,
    next_x = next_x,
    node = node,
    next_node = next_node,
    fill = node,
    label = as.character(node)
  )
) +
  geom_sankey(node.alpha = 0.8, flow.alpha = 0.6) +
  geom_sankey_label(size = 6, alpha = 0.8, fontface = "bold") +
  labs(x = "") +
  scale_fill_manual(values = cols) +
  # scale_x_discrete(expand = c(0, 0)) +
  # scale_y_discrete(expand = c(0, 0)) +
  # coord_cartesian(clip = "off") +
  theme_sankey(base_size = 20) +
  theme(
    legend.position = "none",
    panel.background = element_blank(),
    panel.border = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    plot.background = element_blank(),
    plot.margin = margin(0, 0, 0, 0),
    panel.margin = margin(0, 0, 0, 0),
  )


# sank

ggsave(
  plot = sank,
  filename = file.path(imgdir, "sankey_plot_clustering.pdf"),
  width = 2700,
  height = 3200,
  device = cairo_pdf,
  units = "px"
)

ggsave(
  plot = sank,
  filename = file.path(imgdir, "sankey_plot_clustering.png"),
  width = 2700,
  height = 3200,
  units = "px"
)
```

```{r}

top_b <- cabic@gene_ranks$B_cell %>%
  filter(Score > 0)
gs <- CAbiNet:::load_gene_set(set = "CellMarker", org = "hs")
gs_bcells <- gs %>%
  filter(cell_type == "B cell") %>%
  pull(gene) %>%
  unique()

cat("% of B cell marker genes:", mean(top_b$Rowname %in% gs_bcells), "\n")
```

```{r}
top_m <- cabic@gene_ranks$Monocyte %>%
  filter(Score > 0)
gs <- CAbiNet:::load_gene_set(set = "CellMarker", org = "hs")
gs_mono <- gs %>%
  filter(cell_type == "Monocyte") %>%
  pull(gene) %>%
  unique()

cat("% of Monocyte marker genes:", mean(top_m$Rowname %in% gs_mono), "\n")
```

```{r}
top_t <- cabic@gene_ranks$`CD8+_T_cell` %>%
  filter(Score > 0)
gs <- CAbiNet:::load_gene_set(set = "CellMarker", org = "hs")
gs_tcells <- gs %>%
  filter(cell_type == "CD8+ T cell") %>%
  pull(gene) %>%
  unique()

cat("% of CD8+ T cells marker genes:", mean(top_t$Rowname %in% gs_tcells), "\n")
```

```{r}
# top_nk <- cabic@gene_ranks$Natural_killer_cell %>%
#   filter(Score > 0)
#
# gs <- CAbiNet:::load_gene_set(set = "CellMarker", org = "hs")
# gs_nkcells <- gs %>%
#   filter(cell_type == "Natural killer cell") %>%
#   pull(gene) %>%
#   unique()
#
# cat("% of NK cells marker genes:", mean(top_nk$Rowname %in% gs_nkcells), "\n")
```



```{r}
top_nk <- cabic@gene_ranks$`Cytotoxic_CD4+_T_cell` %>%
  filter(Score > 0)

gs <- CAbiNet:::load_gene_set(set = "CellMarker", org = "hs")
gs_nkcells <- gs %>%
  filter(cell_type == "Cytotoxic CD4+ T cell") %>%
  pull(gene) %>%
  unique()

cat("% of NK cells marker genes:", mean(top_nk$Rowname %in% gs_nkcells), "\n")
```


```{r}
top_mega <- cabic@gene_ranks$Megakaryocyte %>%
  filter(Score > 0)

gs <- CAbiNet:::load_gene_set(set = "CellMarker", org = "hs")
gs_mkcells <- gs %>%
  filter(cell_type == "Megakaryocyte") %>%
  pull(gene) %>%
  unique()

cat(
  "% of Megakaryocyte marker genes:",
  mean(top_mega$Rowname %in% gs_mkcells),
  "\n"
)
```

```{r}
# top_c6 <- cabic@gene_ranks$cluster_5
top_naive <- cabic@gene_ranks$`Naive_CD4+_T_cell`

gs <- CAbiNet:::load_gene_set(set = "CellMarker", org = "hs")
gs_cd4tcells <- gs %>%
  filter(cell_type == "Naive CD4+ T cell") %>%
  pull(gene) %>%
  unique()

cat("% of cd4 marker genes:", mean(top_naive$Rowname %in% gs_cd4tcells), "\n")
```

```{r}
# top_mega <- cabic@gene_ranks$Megakaryocyte %>%
#   filter(Score > 0)
#
# gs <- CAbiNet:::load_gene_set(set = "CellMarker", org = "hs")
# gs_plate <- gs %>%
#   filter(cell_type == "Platelet") %>%
#   pull(gene) %>%
#   unique()
#
# cat("% of Platelet marker genes:", mean(top_mega$Rowname %in% gs_plate), "\n")
```

```{r}
top_dend <- cabic@gene_ranks$`Dendritic_cell` %>%
  filter(Score > 0)

gs <- CAbiNet:::load_gene_set(set = "CellMarker", org = "hs")
gs_dend <- gs %>%
  filter(cell_type == "Dendritic cell") %>%
  pull(gene) %>%
  unique()

cat("% of Dendritic marker genes:", mean(top_dend$Rowname %in% gs_dend), "\n")
```


```{r}
# unique(gs$cell_type)[grep("T cell", unique(gs$cell_type))]
```

```{r}
cm <- CAbiNet::cellmarker_v2
cm <- cm[cm$species == "Human", ]
cm <- cm[cm$cell_name == "B cell", ]
```

# Pie charts

```{r}
# perc1 <- mean(top_b$Rowname %in% gs_bcells)
# perc1
# # pie(c(perc1, 1 - perc1), labels = c("Markers", "Other"), col = rev(CAdir::mpimg_pal()(2)))
#
# perc2 <- mean(top_t$Rowname %in% gs_tcells)
# perc2
# # pie(c(perc2, 1 - perc2), labels = c("Markers", "Other"), col = rev(CAdir::mpimg_pal()(2)))
#
# perc3 <- mean(top_m$Rowname %in% gs_mono)
# perc3
# # pie(c(perc3, 1 - perc3), labels = c("Markers", "Other"), col = rev(CAdir::mpimg_pal()(2)))
#
# perc4 <- mean(top_nk$Rowname %in% gs_nkcells)
# perc4
# # pie(c(perc4, 1 - perc4), labels = c("Markers", "Other"), col = rev(CAdir::mpimg_pal()(2)))
#
# perc5 <- mean(top_mega$Rowname %in% gs_mkcells)
# perc5
# # pie(c(perc5, 1 - perc5), labels = c("Markers", "Other"), col = rev(CAdir::mpimg_pal()(2)))
#
# perc6 <- mean(top_dend$Rowname %in% gs_dend)
# perc6
#
# perc7 <- mean(top_naive$Rowname %in% gs_cd4tcells)
# perc7
```

```{r}
library(gridGraphics)

piechart <- function(perc, title) {
  pie(
    x = c(perc, 1 - perc),
    labels = c("Markers", "Other"),
    col = rev(CAdir::mpimg_pal()(2))
  )
  title(main = title, cex.main = 1.2, line = 0.1)
}

perc1 <- mean(top_b$Rowname %in% gs_bcells)
pie1 <- wrap_elements(full = ~ piechart(perc1, "B cells"))
perc1

perc2 <- mean(top_t$Rowname %in% gs_tcells)
pie2 <- wrap_elements(full = ~ piechart(perc2, "CD8+ T cells"))
perc2

perc3 <- mean(top_m$Rowname %in% gs_mono)
pie3 <- wrap_elements(full = ~ piechart(perc3, "Monocytes"))
perc3

perc4 <- mean(top_nk$Rowname %in% gs_nkcells)
pie4 <- wrap_elements(full = ~ piechart(perc4, "Cytotoxic CD4+ T cell"))
perc4

perc5 <- mean(top_mega$Rowname %in% gs_mkcells)
pie5 <- wrap_elements(full = ~ piechart(perc5, "Megakaryocytes"))
perc5

perc6 <- mean(top_dend$Rowname %in% gs_dend)
pie6 <- wrap_elements(full = ~ piechart(perc6, "Dendritic cells"))
perc6

perc7 <- mean(top_naive$Rowname %in% gs_cd4tcells)
pie7 <- wrap_elements(full = ~ piechart(perc7, "Naive CD4+ T cells"))
perc7

pdf(file = file.path(imgdir, "pies.pdf"), width = 9, height = 6)
(pie1 + pie2 + pie3 + pie4 + pie6 + pie5 + pie7) +
  plot_layout(ncol = 4) +
  plot_annotation(tag_levels = "a")
dev.off()

png(
  file = file.path(imgdir, "pies.png"),
  width = 900,
  height = 600,
  units = "px"
)
(pie1 + pie2 + pie3 + pie4 + pie6 + pie5 + pie7) +
  plot_layout(ncol = 4) +
  plot_annotation(tag_levels = "a")
dev.off()
```

# Pie + Sankey
```{r}
# pdf(file = file.path(imgdir, "pies_and_sankey.pdf"), width = 12, height = 6)
# ((pie1 + pie2 + pie3 + pie4 + pie5) | sank) +
#   plot_annotation(tag_levels = "a") &
#   theme(plot.tag = element_text(size = 16))
# dev.off()

pc <- (pie1 + pie2 + pie3 + pie4 + pie6 + pie5 + pie7) +
  plot_layout(ncol = 4) +
  plot_annotation(tag_levels = "a")

layout <- c(
  area(t = 1, b = 8, l = 1, r = 12),
  area(t = 1, b = 8, l = 14, r = 17),
  area(t = 1, b = 8, l = 18, r = 18)
)

png(
  file = file.path(imgdir, "pies_and_sankey.png"),
  width = 1200,
  height = 600,
  units = "px"
)
(pc | sank4panel) +
  plot_layout(width = c(2, 1)) +
  # plot_layout(design = layout) +
  plot_annotation(tag_levels = "a") &
  theme(
    plot.tag = element_text(size = 18, face = "bold"),
    title = element_text(size = 16)
  )
dev.off()
```

# B cell discussion
```{r}
top_b
top_m
```

# Top genes table

```{r}
library(xtable)
tbl <- top_genes(cabic, cutoff = 0)

top_table <- list()
n <- 3
for (c in unique(tbl$Cluster)) {
  cat(c)
  sub_tbl <- tbl[tbl$Cluster == c, ] %>%
    dplyr::arrange(desc(Score))
  top_table[[c]] <- sub_tbl[seq(n), ]
}
top_table <- do.call("rbind", top_table)
top_table <- top_table[, c(1, 2, 4)]
colnames(top_table) <- c("Gene", "Score", "Cluster")
top_table <- top_table[, c("Cluster", "Gene", "Score")]
rownames(top_table) <- NULL
print(
  xtable(top_table, type = "latex"),
  file = file.path(imgdir, "top_genes.tex")
)
```

# Marker genes
```{r}
rnks <- cabic@gene_ranks
markers <- scoreMarkers(sce, sce$cadir)
```

## B cells
```{r}
cadir_bcell <- cabic@gene_ranks$B_cell
cadir_score <- cadir_bcell[cadir_bcell$Score > 0, ]
bdegs <- markers$B_cell[
  order(markers$B_cell$mean.AUC, decreasing = TRUE),
]
bp1 <- plotExpression(
  sce,
  features = head(cadir_score$Rowname, 4),
  x = "cadir",
  colour_by = "cadir"
) +
  scale_color_mpimg() +
  labs(x = "Clusters")

bp2 <- plotExpression(
  sce,
  features = head(rownames(bdegs), 4),
  x = "cadir",
  colour_by = "cadir"
) +
  scale_color_mpimg() +
  labs(x = "Clusters")

bp1 + bp2

ggsave(
  plot = bp1,
  filename = file.path(imgdir, "bcell_cadir_markers.png"),
  device = cairo_pdf,
  width = 3000,
  height = 3000,
  units = "px"
)

ggsave(
  plot = bp2,
  filename = file.path(imgdir, "bcell_bioconductor_markers.png"),
  device = cairo_pdf,
  width = 3000,
  height = 3000,
  units = "px"
)
```

## Naive CD4 T cells
```{r}
cadir_cd4 <- cabic@gene_ranks$`Naive_CD4+_T_cell`
cadir_score <- cadir_cd4[cadir_cd4$Score > 0, ]
cd4degs <- markers$`Naive_CD4+_T_cell`[
  order(markers$`Naive_CD4+_T_cell`$mean.AUC, decreasing = TRUE),
]
cd4p1 <- plotExpression(
  sce,
  features = head(cadir_score$Rowname, 4),
  x = "cadir",
  colour_by = "cadir"
) +
  scale_color_mpimg() +
  labs(x = "Clusters")

cd4p2 <- plotExpression(
  sce,
  features = head(rownames(cd4degs), 4),
  x = "cadir",
  colour_by = "cadir"
) +
  scale_color_mpimg() +
  labs(x = "Clusters")

cd4p1 + cd4p2

ggsave(
  plot = cd4p1,
  filename = file.path(imgdir, "cd4_cadir_markers.png"),
  device = cairo_pdf,
  width = 3000,
  height = 3000,
  units = "px"
)

ggsave(
  plot = cd4p2,
  filename = file.path(imgdir, "cd4_bioconductor_markers.png"),
  device = cairo_pdf,
  width = 3000,
  height = 3000,
  units = "px"
)
```

## Monocytes
```{r}
cadir_mono <- cabic@gene_ranks$Monocyte
cadir_score <- cadir_mono[cadir_mono$Score > 0, ]
monodegs <- markers$Monocyte[
  order(markers$Monocyte$mean.AUC, decreasing = TRUE),
]
monop1 <- plotExpression(
  sce,
  features = head(cadir_score$Rowname, 4),
  x = "cadir",
  colour_by = "cadir"
) +
  scale_color_mpimg() +
  labs(x = "Clusters")

monop2 <- plotExpression(
  sce,
  features = head(rownames(monodegs), 4),
  x = "cadir",
  colour_by = "cadir"
) +
  scale_color_mpimg() +
  labs(x = "Clusters")

monop1 + monop2

ggsave(
  plot = monop1,
  filename = file.path(imgdir, "monocytes_cadir_markers.png"),
  device = cairo_pdf,
  width = 3000,
  height = 3000,
  units = "px"
)

ggsave(
  plot = monop2,
  filename = file.path(imgdir, "monocytes_bioconductor_markers.png"),
  device = cairo_pdf,
  width = 3000,
  height = 3000,
  units = "px"
)
```

## Megakaryocyte
```{r}
cadir_mega <- cabic@gene_ranks$Megakaryocyte
cadir_score <- cadir_mega[cadir_mega$Score > 0, ]
megadegs <- markers$Megakaryocyte[
  order(markers$Megakaryocyte$mean.AUC, decreasing = TRUE),
]
megap1 <- plotExpression(
  sce,
  features = head(cadir_score$Rowname, 4),
  x = "cadir",
  colour_by = "cadir"
) +
  scale_color_mpimg() +
  labs(x = "Clusters")

megap2 <- plotExpression(
  sce,
  features = head(rownames(megadegs), 4),
  x = "cadir",
  colour_by = "cadir"
) +
  scale_color_mpimg() +
  labs(x = "Clusters")

megap1 + megap2

ggsave(
  plot = megap1,
  filename = file.path(imgdir, "megakaryocytes_cadir_markers.png"),
  device = cairo_pdf,
  width = 3000,
  height = 3000,
  units = "px"
)

ggsave(
  plot = megap2,
  filename = file.path(imgdir, "megakaryocytes_bioconductor_markers.png"),
  device = cairo_pdf,
  width = 3000,
  height = 3000,
  units = "px"
)
```

## Dendritic Cell
```{r}
cadir_dend <- cabic@gene_ranks$Dendritic_cell
cadir_score <- cadir_dend[cadir_dend$Score > 0, ]
denddegs <- markers$Dendritic_cell[
  order(markers$Dendritic_cell$mean.AUC, decreasing = TRUE),
]
dendp1 <- plotExpression(
  sce,
  features = head(cadir_score$Rowname, 4),
  x = "cadir",
  colour_by = "cadir"
) +
  scale_color_mpimg() +
  labs(x = "Clusters")

dendp2 <- plotExpression(
  sce,
  features = head(rownames(denddegs), 4),
  x = "cadir",
  colour_by = "cadir"
) +
  scale_color_mpimg() +
  labs(x = "Clusters")

dendp1 + dendp2

ggsave(
  plot = dendp1,
  filename = file.path(imgdir, "dendritic_cells_cadir_markers.png"),
  device = cairo_pdf,
  width = 3000,
  height = 3000,
  units = "px"
)

ggsave(
  plot = dendp2,
  filename = file.path(imgdir, "dendritic_cells_bioconductor_markers.png"),
  device = cairo_pdf,
  width = 3000,
  height = 3000,
  units = "px"
)
```

## CD8+ T cells
```{r}
cadir_cd8 <- cabic@gene_ranks$`CD8+_T_cell`
cadir_score <- cadir_cd8[cadir_cd8$Score > 0, ]
cd8degs <- markers$`CD8+_T_cell`[
  order(markers$`CD8+_T_cell`$mean.AUC, decreasing = TRUE),
]
cd8p1 <- plotExpression(
  sce,
  features = head(cadir_score$Rowname, 4),
  x = "cadir",
  colour_by = "cadir"
) +
  scale_color_mpimg() +
  labs(x = "Clusters")

cd8p2 <- plotExpression(
  sce,
  features = head(rownames(cd8degs), 4),
  x = "cadir",
  colour_by = "cadir"
) +
  scale_color_mpimg() +
  labs(x = "Clusters")

cd8p1 + cd8p2

ggsave(
  plot = cd8p1,
  filename = file.path(imgdir, "cd8_t_cells_cadir_markers.png"),
  device = cairo_pdf,
  width = 3000,
  height = 3000,
  units = "px"
)

ggsave(
  plot = cd8p2,
  filename = file.path(
    imgdir,
    "cd8_t_cells_bioconductor_markers.png"
  ),
  device = cairo_pdf,
  width = 3000,
  height = 3000,
  units = "px"
)
```

## Cytotoxic CD4+ T cell
```{r}
cadir_ctcd4 <- cabic@gene_ranks$`Cytotoxic_CD4+_T_cell`
cadir_score <- cadir_ctcd4[cadir_ctcd4$Score > 0, ]
ctcd4degs <- markers$`Cytotoxic_CD4+_T_cell`[
  order(markers$`Cytotoxic_CD4+_T_cell`$mean.AUC, decreasing = TRUE),
]
ctcd4p1 <- plotExpression(
  sce,
  features = head(cadir_score$Rowname, 4),
  x = "cadir",
  colour_by = "cadir"
) +
  scale_color_mpimg() +
  labs(x = "Clusters")

ctcd4p2 <- plotExpression(
  sce,
  features = head(rownames(ctcd4degs), 4),
  x = "cadir",
  colour_by = "cadir"
) +
  scale_color_mpimg() +
  labs(x = "Clusters")

ctcd4p1 + ctcd4p2

ggsave(
  plot = ctcd4p1,
  filename = file.path(imgdir, "cytotoxic_cd4_t_cells_cadir_markers.png"),
  device = cairo_pdf,
  width = 3000,
  height = 3000,
  units = "px"
)

ggsave(
  plot = ctcd4p2,
  filename = file.path(
    imgdir,
    "cytotoxic_cd4_t_cells_bioconductor_markers.png"
  ),
  device = cairo_pdf,
  width = 3000,
  height = 3000,
  units = "px"
)
```

## Comparison CAdir vs ScoreMarkers 

```{r}
rnks <- cabic@gene_ranks
markers <- scoreMarkers(sce, sce$cadir)

mat <- matrix(NA, nrow = length(rnks), ncol = length(rnks))
rownames(mat) <- names(rnks)
colnames(mat) <- names(rnks)

shared_genes <- as_tibble(mat)
perc_shared <- mat

for (i in seq_len(length(names(rnks)))) {
  c <- names(rnks)[i]
  cadir_genes <- rnks[[c]]$Rowname
  ngenes <- length(cadir_genes)

  for (j in seq_len(length(names(rnks)))) {
    d <- names(rnks)[j]
    cls_markers <- markers[[d]]
    cls_markers$Gene <- rownames(cls_markers)
    cls_markers <- cls_markers[cls_markers$mean.AUC >= 0.5, ]

    cls_markers <- cls_markers[
      order(cls_markers$mean.AUC, decreasing = TRUE),
    ]
    degs <- cls_markers$Gene[seq_len(ngenes)]

    overlap <- intersect(cadir_genes, degs)

    shared_genes[[c]][j] <- list(overlap)
    perc_shared[j, i] <- length(overlap) / ngenes
  }
}
```

```{r}
df <- as_tibble(perc_shared)
df$scoreMarkers <- colnames(df)

df <- df %>%
  pivot_longer(names_to = "CAdir", values_to = "overlap", cols = -scoreMarkers)

p_shared <- ggplot(df, aes(x = CAdir, y = scoreMarkers, fill = overlap)) +
  geom_tile() +
  coord_fixed() +
  CAdir:::scale_fill_gradient_mpimg(name = "orange") +
  theme_bw()

# p_shared

ggsave(
  plot = p_shared,
  filename = file.path(imgdir, "deg_comp.pdf"),
  device = cairo_pdf,
  width = 3000,
  height = 3000,
  units = "px"
)
```

## Comparison CAdir vs ScoreMarkers - S-alpha > 0
```{r}
rnks <- cabic@gene_ranks
markers <- scoreMarkers(sce, sce$cadir)

mat <- matrix(NA, nrow = length(rnks), ncol = length(rnks))
rownames(mat) <- names(rnks)
colnames(mat) <- names(rnks)

shared_genes <- as_tibble(mat)
perc_shared <- mat

for (i in seq_len(length(names(rnks)))) {
  c <- names(rnks)[i]
  cadir_genes <- rnks[[c]]
  cadir_genes <- cadir_genes[cadir_genes$Score > 0, ]
  cadir_genes <- cadir_genes$Rowname
  ngenes <- length(cadir_genes)

  for (j in seq_len(length(names(rnks)))) {
    d <- names(rnks)[j]
    cls_markers <- markers[[d]]
    cls_markers$Gene <- rownames(cls_markers)
    cls_markers <- cls_markers[cls_markers$mean.AUC >= 0.5, ]

    cls_markers <- cls_markers[
      order(cls_markers$mean.AUC, decreasing = TRUE),
    ]
    degs <- cls_markers$Gene[seq_len(ngenes)]

    overlap <- intersect(cadir_genes, degs)

    shared_genes[[c]][j] <- list(overlap)
    perc_shared[j, i] <- length(overlap) / ngenes
  }
}
```

```{r}
df <- as_tibble(perc_shared)
df$scoreMarkers <- colnames(df)

df <- df %>%
  pivot_longer(names_to = "CAdir", values_to = "overlap", cols = -scoreMarkers)

p_salpha <- ggplot(df, aes(x = CAdir, y = scoreMarkers, fill = overlap)) +
  geom_tile() +
  coord_fixed() +
  CAdir:::scale_fill_gradient_mpimg(name = "orange") +
  theme_bw()

# p_salpha

ggsave(
  plot = p_salpha,
  filename = file.path(imgdir, "deg_comp_pos_salpha.pdf"),
  device = cairo_pdf,
  width = 3000,
  height = 3000,
  units = "px"
)
```

# Panels

```{r}
bmarkers <- (bp1 + ggtitle("CAdir: Top 4 genes - B cells")) +
  plot_spacer() +
  (bp2 + ggtitle("scran: Top 4 genes - B cells")) +
  plot_layout(
    guides = "collect",
    # axis = "collect",
    width = c(19, 1, 19)
  ) +
  plot_annotation(tag_levels = "a") &
  theme(
    plot.tag = element_text(size = 18, face = "bold"),
    title = element_text(size = 16),
    axis.text.x = element_text(size = 12, angle = 45, hjust = 1),
    legend.position = "none",
    strip.text.x = element_text(
      size = 14,
      face = "bold"
    ),
    strip.text.y = element_text(
      size = 14,
      face = "bold"
    )
  )

ggsave(
  plot = bmarkers,
  filename = file.path(imgdir, "bcell_markers_panel.png"),
  width = 5200,
  height = 2400,
  units = "px"
)

ggsave(
  plot = bmarkers,
  filename = file.path(imgdir, "bcell_markers_panel.pdf"),
  device = cairo_pdf,
  width = 5200,
  height = 2400,
  units = "px"
)
```

```{r}

cd4markers <- (cd4p1 + ggtitle("CAdir: Top 4 genes - Naive CD4+ T cells")) +
  plot_spacer() +
  (cd4p2 + ggtitle("scran: Top 4 genes - Naive CD4+ T cells")) +
  plot_layout(
    guides = "collect",
    # axis = "collect",
    width = c(19, 1, 19)
  ) +
  plot_annotation(tag_levels = "a") &
  theme(
    plot.tag = element_text(size = 18, face = "bold"),
    title = element_text(size = 16),
    axis.text.x = element_text(size = 12, angle = 45, hjust = 1),
    legend.position = "none",
    strip.text.x = element_text(
      size = 14,
      face = "bold"
    ),
    strip.text.y = element_text(
      size = 14,
      face = "bold"
    )
  )

ggsave(
  plot = cd4markers,
  filename = file.path(imgdir, "cd4tcells_markers_panel.png"),
  width = 5200,
  height = 2400,
  units = "px"
)

ggsave(
  plot = cd4markers,
  filename = file.path(imgdir, "cd4tcells_markers_panel.pdf"),
  device = cairo_pdf,
  width = 5200,
  height = 2400,
  units = "px"
)
```

```{r}
monomarkers <- (monop1 + ggtitle("CAdir: Top 4 genes - Monocytes")) +
  plot_spacer() +
  (monop2 + ggtitle("scran: Top 4 genes - Monocytes")) +
  plot_layout(
    guides = "collect",
    # axis = "collect",
    width = c(19, 1, 19)
  ) +
  plot_annotation(tag_levels = "a") &
  theme(
    plot.tag = element_text(size = 18, face = "bold"),
    title = element_text(size = 16),
    axis.text.x = element_text(size = 12, angle = 45, hjust = 1),
    legend.position = "none",
    strip.text.x = element_text(
      size = 14,
      face = "bold"
    ),
    strip.text.y = element_text(
      size = 14,
      face = "bold"
    )
  )

ggsave(
  plot = monomarkers,
  filename = file.path(imgdir, "monocytes_markers_panel.png"),
  width = 5200,
  height = 2400,
  units = "px"
)

ggsave(
  plot = monomarkers,
  filename = file.path(imgdir, "monocytes_markers_panel.pdf"),
  device = cairo_pdf,
  width = 5200,
  height = 2400,
  units = "px"
)
```

```{r}
megamarkers <- (megap1 + ggtitle("CAdir: Top 4 genes - Megakaryocytes")) +
  plot_spacer() +
  (megap2 + ggtitle("scran: Top 4 genes - Megakaryocytes")) +
  plot_layout(
    guides = "collect",
    # axis = "collect",
    width = c(19, 1, 19)
  ) +
  plot_annotation(tag_levels = "a") &
  theme(
    plot.tag = element_text(size = 18, face = "bold"),
    title = element_text(size = 16),
    axis.text.x = element_text(size = 12, angle = 45, hjust = 1),
    legend.position = "none",
    strip.text.x = element_text(
      size = 14,
      face = "bold"
    ),
    strip.text.y = element_text(
      size = 14,
      face = "bold"
    )
  )

ggsave(
  plot = megamarkers,
  filename = file.path(imgdir, "megakaryocytes_markers_panel.png"),
  width = 5200,
  height = 2400,
  units = "px"
)

ggsave(
  plot = megamarkers,
  filename = file.path(imgdir, "megakaryocytes_markers_panel.pdf"),
  device = cairo_pdf,
  width = 5200,
  height = 2400,
  units = "px"
)
```

```{r}
dendmarkers <- (dendp1 + ggtitle("CAdir: Top 4 genes - Dendritic cells")) +
  plot_spacer() +
  (dendp2 + ggtitle("scran: Top 4 genes - Dendritic cells")) +
  plot_layout(
    guides = "collect",
    # axis = "collect",
    width = c(19, 1, 19)
  ) +
  plot_annotation(tag_levels = "a") &
  theme(
    plot.tag = element_text(size = 18, face = "bold"),
    title = element_text(size = 16),
    axis.text.x = element_text(size = 12, angle = 45, hjust = 1),
    legend.position = "none",
    strip.text.x = element_text(
      size = 14,
      face = "bold"
    ),
    strip.text.y = element_text(
      size = 14,
      face = "bold"
    )
  )

ggsave(
  plot = dendmarkers,
  filename = file.path(imgdir, "dendritic_cells_markers_panel.png"),
  width = 5200,
  height = 2400,
  units = "px"
)

ggsave(
  plot = dendmarkers,
  filename = file.path(imgdir, "dendritic_cells_markers_panel.pdf"),
  device = cairo_pdf,
  width = 5200,
  height = 2400,
  units = "px"
)
```

```{r}
cd8markers <- (cd8p1 + ggtitle("CAdir: Top 4 genes - CD8+ T cells")) +
  plot_spacer() +
  (cd8p2 + ggtitle("scran: Top 4 genes - CD8+ T cells")) +
  plot_layout(
    guides = "collect",
    # axis = "collect",
    width = c(19, 1, 19)
  ) +
  plot_annotation(tag_levels = "a") &
  theme(
    plot.tag = element_text(size = 18, face = "bold"),
    title = element_text(size = 16),
    axis.text.x = element_text(size = 12, angle = 45, hjust = 1),
    legend.position = "none",
    strip.text.x = element_text(
      size = 14,
      face = "bold"
    ),
    strip.text.y = element_text(
      size = 14,
      face = "bold"
    )
  )

ggsave(
  plot = cd8markers,
  filename = file.path(imgdir, "cd8_t_cells_markers_panel.png"),
  width = 5200,
  height = 2400,
  units = "px"
)

ggsave(
  plot = cd8markers,
  filename = file.path(imgdir, "cd8_t_cells_markers_panel.pdf"),
  device = cairo_pdf,
  width = 5200,
  height = 2400,
  units = "px"
)
```
```{r}
ctcd4markers <- (ctcd4p1 +
  ggtitle("CAdir: Top 4 genes - Cytotoxic CD4+ T cells")) +
  plot_spacer() +
  (ctcd4p2 + ggtitle("scran: Top 4 genes - Cytotoxic CD4+ T cells")) +
  plot_layout(
    guides = "collect",
    # axis = "collect",
    width = c(19, 1, 19)
  ) +
  plot_annotation(tag_levels = "a") &
  theme(
    plot.tag = element_text(size = 18, face = "bold"),
    title = element_text(size = 16),
    axis.text.x = element_text(size = 12, angle = 45, hjust = 1),
    legend.position = "none",
    strip.text.x = element_text(
      size = 14,
      face = "bold"
    ),
    strip.text.y = element_text(
      size = 14,
      face = "bold"
    )
  )

ggsave(
  plot = ctcd4markers,
  filename = file.path(imgdir, "cytotoxic_cd4_t_cells_markers_panel.png"),
  width = 5200,
  height = 2400,
  units = "px"
)

ggsave(
  plot = ctcd4markers,
  filename = file.path(imgdir, "cytotoxic_cd4_t_cells_markers_panel.pdf"),
  device = cairo_pdf,
  width = 5200,
  height = 2400,
  units = "px"
)
```

```{r}
ctcd4markers <- (ctcd4p1 +
  ggtitle("CAdir: Top 4 genes - Cytotoxic CD4+ T cells")) +
  plot_spacer() +
  (ctcd4p2 + ggtitle("scran: Top 4 genes - Cytotoxic CD4+ T cells")) +
  plot_layout(
    guides = "collect",
    # axis = "collect",
    width = c(19, 1, 19)
  ) +
  plot_annotation(tag_levels = "a") &
  theme(
    plot.tag = element_text(size = 18, face = "bold"),
    title = element_text(size = 16),
    axis.text.x = element_text(size = 12, angle = 45, hjust = 1),
    legend.position = "none",
    strip.text.x = element_text(
      size = 14,
      face = "bold"
    ),
    strip.text.y = element_text(
      size = 14,
      face = "bold"
    )
  )

ggsave(
  plot = ctcd4markers,
  filename = file.path(imgdir, "cytotoxic_cd4_t_cells_markers_panel.png"),
  width = 5200,
  height = 2400,
  units = "px"
)

ggsave(
  plot = ctcd4markers,
  filename = file.path(imgdir, "cytotoxic_cd4_t_cells_markers_panel.pdf"),
  device = cairo_pdf,
  width = 5200,
  height = 2400,
  units = "px"
)
```



## DEG comparison
```{r}
deg_comp_panel <- (p_shared +
  ggtitle(
    "Overlap between scran and CAdir",
    subtitle = "all co-clustered genes"
  )) +
  (p_salpha +
    ggtitle(
      "Overlap between scran and CAdir",
      subtitle = "genes with Sα-score > 0"
    )) +
  plot_layout(guides = "collect") +
  plot_annotation(tag_levels = "a") &
  theme(
    plot.tag = element_text(size = 18, face = "bold"),
    title = element_text(size = 14),
    axis.text.x = element_text(
      size = 10,
      angle = 45,
      hjust = 1,
      color = "black"
    ),
    axis.text.y = element_text(
      size = 10,
      # angle = 45,
      # hjust = 1,
      color = "black"
    ),
  )

ggsave(
  plot = deg_comp_panel,
  filename = file.path(imgdir, "deg_comp_panel_panel.png"),
  width = 4000,
  height = 2000,
  units = "px"
)

ggsave(
  plot = deg_comp_panel,
  filename = file.path(imgdir, "deg_comp_panel_panel.pdf"),
  device = cairo_pdf,
  width = 4000,
  height = 2000,
  units = "px"
)
```


# Session Info
```{r}
sessionInfo()
```

