---
title: Sparse simulated data
jupyter:
  jupytext:
    formats: 'ipynb,qmd:quarto'
    text_representation:
      extension: .qmd
      format_name: quarto
      format_version: '1.0'
      jupytext_version: 1.16.1
  kernelspec:
    display_name: R 4.4.1
    language: R
    name: ir441
---

# Setup

```{r}
# Working directory should be the root directory of repository.
# setwd("./")
renv::load()

suppressPackageStartupMessages({
  devtools::load_all("~/gits/ClemensKohl/CAdir/")
  # library(CAdir)
  library(scater)
  library(dplyr)
  library(tidyr)
  library(readr)
  library(ggplot2)
  library(patchwork)
  library(ggthemes)
})

dir <- "./results/"
imgdir <- file.path(dir, "img/review/sparse_bench/")

dir.create(imgdir, recursive = TRUE)

options(repr.plot.width = 20, repr.plot.height = 15)
```

# Cell clustering benchmarking

```{r}
date <- "20251121"
# date <- "20251204"
base_dir <- file.path("./results/benchmarking/results/simulated_sparse", date)
indir <- file.path(base_dir, "eval")
```

## simulated data
Benchmarking results based on Zeisel Brain data:

```{r}
zeisel_eval <- readRDS(
  file.path(
    indir,
    paste0(date, "_zeisel_collated.rds")
  )
)

dfz <- zeisel_eval %>%
  mutate(dataset = "zeisel") %>%
  mutate(simulation = paste(dePROB, defacLOC, defacSCALE, sep = "_")) %>%
  mutate(
    simulation = factor(
      simulation,
      levels = c(
        "0.02_0.75_0.75",
        "0.06_0.75_0.75",
        "0.1_0.75_0.75",
        "0.02_1.5_1.5",
        "0.06_1.5_1.5",
        "0.1_1.5_1.5"
      )
    )
  )

table(
  zeisel_eval$algorithm,
  paste(
    zeisel_eval$dePROB,
    zeisel_eval$defacLOC,
    zeisel_eval$defacSCALE,
    sep = "_"
  )
)
```

Benchmarking results based on PBMC3k data:

```{r}
pbmc_eval <- readRDS(
  file.path(
    indir,
    paste0(date, "_pbmc3k_collated.rds")
  )
)

dfp <- pbmc_eval %>%
  mutate(dataset = "pbmc3k") %>%
  mutate(simulation = paste(dePROB, defacLOC, defacSCALE, sep = "_")) %>%
  mutate(
    simulation = factor(
      simulation,
      levels = c(
        "0.02_0.75_0.75",
        "0.06_0.75_0.75",
        "0.1_0.75_0.75",
        "0.02_1.5_1.5",
        "0.06_1.5_1.5",
        "0.1_1.5_1.5"
      )
    )
  )

table(
  pbmc_eval$algorithm,
  paste(pbmc_eval$dePROB, pbmc_eval$defacLOC, pbmc_eval$defacSCALE, sep = "_")
)
```

Combining the benchmarking resuls:

```{r}
df_all <- rbind(dfz, dfp)

df_all$algorithm <- gsub("CAbiNet_igraph", "CAbiNet", df_all$algorithm)

df_all$algorithm <- factor(
  df_all$algorithm,
  levels = c(
    "CAdir",
    "CAdir_auto",
    "kmeans",
    "CAbiNet",
    "RaceID",
    "RaceID_auto",
    "Seurat",
    "Monocle3",
    "SC3",
    "SIMLR",
    "scDeepCluster",
    "scG-cluster"
  )
)


df <- df_all %>%
  group_by(simulation, algorithm, dataset) %>%
  mutate(mean_ARI = mean(ARI, na.rm = TRUE)) %>%
  mutate(mean_NMI = mean(NMI, na.rm = TRUE)) %>%
  select(dataset, simulation, algorithm, mean_ARI, mean_NMI) %>%
  distinct() %>%
  ungroup()
```

### Simulated data benchmarking - Max Results

```{r}
df <- df_all %>%
  group_by(simulation, algorithm, dataset) %>%
  mutate(max_ARI = max(ARI, na.rm = TRUE)) %>%
  mutate(max_NMI = max(NMI, na.rm = TRUE)) %>%
  select(dataset, simulation, algorithm, max_ARI, max_NMI) %>%
  distinct() %>%
  ungroup()

df$max_ARI[is.infinite(df$max_ARI)] <- 0
df$max_NMI[is.infinite(df$max_NMI)] <- 0
```

```{r}
p_max_ari <- df %>%
  ggplot(aes(
    x = algorithm,
    y = max_ARI
  )) +
  geom_boxplot(
    aes(fill = algorithm),
    color = "#383e42",
    alpha = 1,
    outlier.alpha = 0
  ) +
  geom_jitter(
    aes(
      x = algorithm,
      y = max_ARI,
      color = dataset,
      group = dataset,
      shape = simulation
    ),
    stroke = 1.5,
    size = 2,
    width = 0.2
  ) +
  labs(
    title = "Maximum ARI on simulated data",
    y = "max ARI",
    x = "algorithm"
  ) +
  scale_shape_manual(values = seq_len(length(df$simulation))) +
  scale_fill_mpimg(name = "mpi_extend") +
  scale_color_manual(
    values = list("zeisel" = "#60636a", "pbmc3k" = "#a5acaf")
  ) +
  theme_bw(base_size = 20) +
  theme(
    axis.text.x = element_text(
      color = "black",
      angle = 45,
      vjust = 1,
      hjust = 1
    ),
    text = element_text(size = 20),
  ) +
  guides(fill = "none")

# p_max_ari

ggsave(
  plot = p_max_ari,
  filename = file.path(imgdir, "sim_bench_max_ARI_cells.pdf"),
  width = 3000,
  height = 2000,
  units = "px"
)
ggsave(
  plot = p_max_ari,
  filename = file.path(imgdir, "sim_bench_max_ARI_cells.png"),
  width = 3000,
  height = 2000,
  units = "px"
)
```

```{r}
p_max_nmi <- df %>%
  ggplot(aes(
    x = algorithm,
    y = max_NMI
  )) +
  geom_boxplot(
    aes(fill = algorithm),
    color = "#383e42",
    alpha = 1,
    outlier.alpha = 0
  ) +
  geom_jitter(
    aes(
      x = algorithm,
      y = max_NMI,
      color = dataset,
      group = dataset,
      shape = simulation
    ),
    stroke = 1.5,
    size = 2,
    width = 0.2
  ) +
  labs(
    title = "Maximum NMI on simulated data",
    y = "max NMI",
    x = "algorithm"
  ) +
  scale_shape_manual(values = seq_len(length(df$simulation))) +
  scale_fill_mpimg(name = "mpi_extend") +
  scale_color_manual(
    values = list("zeisel" = "#60636a", "pbmc3k" = "#a5acaf")
  ) +
  theme_bw(base_size = 18) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
  guides(fill = "none")

# p_max_nmi

ggsave(
  plot = p_max_nmi,
  filename = file.path(imgdir, "sim_bench_max_NMI_cells.pdf"),
  width = 3000,
  height = 2000,
  units = "px"
)
ggsave(
  plot = p_max_nmi,
  filename = file.path(imgdir, "sim_bench_max_NMI_cells.png"),
  width = 3000,
  height = 2000,
  units = "px"
)
```

### Simulated data benchmarking - Average Results

```{r}
df <- df_all %>%
  group_by(simulation, algorithm, dataset) %>%
  mutate(mean_ARI = mean(ARI, na.rm = TRUE)) %>%
  mutate(mean_NMI = mean(NMI, na.rm = TRUE)) %>%
  select(dataset, simulation, algorithm, mean_ARI, mean_NMI) %>%
  distinct() %>%
  ungroup()
```

```{r}
p_mean_ari <- df %>%
  ggplot(aes(
    x = algorithm,
    y = mean_ARI
  )) +
  geom_boxplot(
    aes(fill = algorithm),
    color = "#383e42",
    alpha = 1,
    outlier.alpha = 0
  ) +
  geom_jitter(
    aes(
      x = algorithm,
      y = mean_ARI,
      color = dataset,
      group = dataset,
      shape = simulation
    ),
    stroke = 1.5,
    size = 2,
    width = 0.2
  ) +
  labs(
    title = "Mean ARI on simulated data",
    y = "mean ARI",
    x = "algorithm"
  ) +
  scale_shape_manual(values = seq_len(length(df$simulation))) +
  scale_fill_mpimg(name = "mpi_extend") +
  scale_color_manual(
    values = list("zeisel" = "#60636a", "pbmc3k" = "#a5acaf")
  ) +
  theme_bw(base_size = 20) +
  theme(
    axis.text.x = element_text(
      color = "black",
      angle = 45,
      vjust = 1,
      hjust = 1
    ),
    text = element_text(size = 20),
  ) +
  guides(fill = "none")

# p_mean_ari

ggsave(
  plot = p_mean_ari,
  filename = file.path(imgdir, "sim_bench_mean_ARI_cells.pdf"),
  width = 2500,
  height = 1650,
  units = "px"
)
ggsave(
  plot = p_mean_ari,
  filename = file.path(imgdir, "sim_bench_mean_ARI_cells.png"),
  width = 2500,
  height = 1650,
  units = "px"
)
```

```{r}
p_mean_nmi <- df %>%
  ggplot(aes(
    x = algorithm,
    y = mean_NMI
  )) +
  geom_boxplot(
    aes(fill = algorithm),
    color = "#383e42",
    alpha = 1,
    outlier.alpha = 0
  ) +
  geom_jitter(
    aes(
      x = algorithm,
      y = mean_NMI,
      color = dataset,
      group = dataset,
      shape = simulation
    ),
    stroke = 1.5,
    size = 2,
    width = 0.2
  ) +
  labs(
    title = "Mean NMI on simulated data",
    y = "mean NMI",
    x = "algorithm"
  ) +
  scale_shape_manual(values = seq_len(length(df$simulation))) +
  scale_fill_mpimg(name = "mpi_extend") +
  scale_color_manual(
    values = list("zeisel" = "#60636a", "pbmc3k" = "#a5acaf")
  ) +
  theme_bw(base_size = 18) +
  theme(
    axis.text.x = element_text(
      color = "black",
      angle = 45,
      vjust = 1,
      hjust = 1
    ),
    text = element_text(size = 20),
  ) +
  guides(fill = "none")

# p_mean_nmi

ggsave(
  plot = p_mean_nmi,
  filename = file.path(imgdir, "sim_bench_mean_NMI_cells.pdf"),
  width = 2500,
  height = 1650,
  units = "px"
)
ggsave(
  plot = p_mean_nmi,
  filename = file.path(imgdir, "sim_bench_mean_NMI_cells.png"),
  width = 2500,
  height = 1650,
  units = "px"
)
```

# Biclustering

```{r}
date <- "20251204"
# date <- "20251121"
base_dir <- file.path(
  "./results/benchmarking/results/biclustering_sparse",
  date
)
indir <- file.path(base_dir, "eval")
```

## simulated data
Benchmarking results based on Zeisel Brain data:

```{r}
zeisel_eval <- readRDS(
  file.path(
    indir,
    paste0(date, "_zeisel_collated.rds")
  )
)

dfz <- zeisel_eval %>%
  mutate(dataset = "zeisel") %>%
  mutate(simulation = paste(dePROB, defacLOC, defacSCALE, sep = "_")) %>%
  mutate(
    simulation = factor(
      simulation,
      levels = c(
        "0.02_0.75_0.75",
        "0.06_0.75_0.75",
        "0.1_0.75_0.75",
        "0.02_1.5_1.5",
        "0.06_1.5_1.5",
        "0.1_1.5_1.5"
      )
    )
  )

table(
  zeisel_eval$algorithm,
  paste(
    zeisel_eval$dePROB,
    zeisel_eval$defacLOC,
    zeisel_eval$defacSCALE,
    sep = "_"
  )
)
```

Benchmarking results based on PBMC3k data:

```{r}
pbmc_eval <- readRDS(
  file.path(
    indir,
    paste0(date, "_pbmc3k_collated.rds")
  )
)

dfp <- pbmc_eval %>%
  mutate(dataset = "pbmc3k") %>%
  mutate(simulation = paste(dePROB, defacLOC, defacSCALE, sep = "_")) %>%
  mutate(
    simulation = factor(
      simulation,
      levels = c(
        "0.02_0.75_0.75",
        "0.06_0.75_0.75",
        "0.1_0.75_0.75",
        "0.02_1.5_1.5",
        "0.06_1.5_1.5",
        "0.1_1.5_1.5"
      )
    )
  )

table(
  pbmc_eval$algorithm,
  paste(pbmc_eval$dePROB, pbmc_eval$defacLOC, pbmc_eval$defacSCALE, sep = "_")
)
```

Combining the benchmarking resuls:

```{r}
df_all <- rbind(dfz, dfp)

df_all$algorithm <- gsub("CAbiNet_igraph", "CAbiNet", df_all$algorithm)
df_all$algorithm <- gsub("nmf", "NMF", df_all$algorithm)
df_all <- df_all %>% filter(algorithm != "kmeans")

df_all$algorithm <- factor(
  df_all$algorithm,
  levels = c(
    "CAdir",
    "CAdir_auto",
    # "kmeans",
    "CAbiNet",
    "Seurat",
    "Monocle3",
    "BackSPIN",
    "CCA",
    "Plaid",
    "QUBIC",
    "s4vd",
    "NMF"
  )
)
df_mean <- df_all %>%
  group_by(simulation, algorithm, dataset) %>%
  mutate(mean_CE = mean(clustering_error, na.rm = TRUE)) %>%
  mutate(mean_ARI_cells = mean(ARI_cells, na.rm = TRUE)) %>%
  mutate(mean_ARI_genes = mean(ARI_genes, na.rm = TRUE)) %>%
  select(
    dataset,
    simulation,
    algorithm,
    mean_CE,
    mean_ARI_cells,
    mean_ARI_genes
  ) %>%
  distinct() %>%
  ungroup()


df_max <- df_all %>%
  group_by(simulation, algorithm, dataset) %>%
  mutate(max_CE = max(clustering_error, na.rm = TRUE)) %>%
  mutate(max_ARI_cells = max(ARI_cells, na.rm = TRUE)) %>%
  mutate(max_ARI_genes = max(ARI_genes, na.rm = TRUE)) %>%
  select(
    dataset,
    simulation,
    algorithm,
    max_CE,
    max_ARI_cells,
    max_ARI_genes
  ) %>%
  distinct() %>%
  ungroup()

df_max$max_CE[is.infinite(df_max$max_CE)] <- 0
df_max$max_ARI_cells[is.infinite(df_max$max_ARI_cells)] <- 0
df_max$max_ARI_cells[is.infinite(df_max$max_ARI_genes)] <- 0
```

### Biclustering - Max Results

```{r}
p_max_ari_bicl <- df_max %>%
  ggplot(aes(
    x = algorithm,
    y = max_ARI_cells
  )) +
  geom_boxplot(
    aes(fill = algorithm),
    color = "#383e42",
    alpha = 1,
    outlier.alpha = 0
  ) +
  geom_jitter(
    aes(
      x = algorithm,
      y = max_ARI_cells,
      color = dataset,
      group = dataset,
      shape = simulation
    ),
    stroke = 1.5,
    size = 2,
    width = 0.2
  ) +
  labs(
    title = "Maximum ARI",
    y = "max ARI",
    x = "algorithm"
  ) +
  scale_shape_manual(values = seq_len(length(df_max$simulation))) +
  scale_fill_mpimg(name = "mpi_extend") +
  scale_color_manual(
    values = list(
      "zeisel" = "#60636a",
      "pbmc3k" = "#a5acaf"
    )
  ) +
  theme_bw(base_size = 18) +
  theme(
    axis.text.x = element_text(
      color = "black",
      angle = 45,
      vjust = 1,
      hjust = 1
    ),
    text = element_text(size = 20),
  ) +
  guides(fill = "none")

# p_max_ari_bicl

ggsave(
  plot = p_max_ari_bicl,
  filename = file.path(imgdir, "bicl_max_ARI_cells.pdf"),
  width = 3000,
  height = 2000,
  units = "px"
)
ggsave(
  plot = p_max_ari_bicl,
  filename = file.path(imgdir, "bicl_max_ARI_cells.png"),
  width = 3000,
  height = 2000,
  units = "px"
)
```

```{r}
p_max_ce_bicl <- df_max %>%
  ggplot(aes(
    x = algorithm,
    y = max_CE
  )) +
  geom_boxplot(
    aes(fill = algorithm),
    color = "#383e42",
    alpha = 1,
    outlier.alpha = 0
  ) +
  geom_jitter(
    aes(
      x = algorithm,
      y = max_CE,
      color = dataset,
      group = dataset,
      shape = simulation
    ),
    stroke = 1.5,
    size = 2,
    width = 0.2
  ) +
  labs(
    title = "Maximum CE",
    y = "max CE",
    x = "algorithm"
  ) +
  scale_shape_manual(values = seq_len(length(df_max$simulation))) +
  scale_fill_mpimg(name = "mpi_extend") +
  scale_color_manual(
    values = list(
      "zeisel" = "#60636a",
      "pbmc3k" = "#a5acaf"
    )
  ) +
  theme_bw(base_size = 18) +
  theme(
    axis.text.x = element_text(
      color = "black",
      angle = 45,
      vjust = 1,
      hjust = 1
    ),
    text = element_text(size = 20),
  ) +
  guides(fill = "none")

# p_max_ce_bicl

ggsave(
  plot = p_max_ce_bicl,
  filename = file.path(imgdir, "bicl_max_CE.pdf"),
  width = 3000,
  height = 2000,
  units = "px"
)
ggsave(
  plot = p_max_ce_bicl,
  filename = file.path(imgdir, "bicl_max_CE.png"),
  width = 3000,
  height = 2000,
  units = "px"
)
```

### Biclustering - Average Results

```{r}
p_mean_ari_bicl <- df_mean %>%
  ggplot(aes(
    x = algorithm,
    y = mean_ARI_cells
  )) +
  geom_boxplot(
    aes(fill = algorithm),
    color = "#383e42",
    alpha = 1,
    outlier.alpha = 0
  ) +
  geom_jitter(
    aes(
      x = algorithm,
      y = mean_ARI_cells,
      color = dataset,
      group = dataset,
      shape = simulation
    ),
    stroke = 1.5,
    size = 2,
    width = 0.2
  ) +
  labs(
    title = "Mean ARI",
    y = "mean ARI",
    x = "algorithm"
  ) +
  scale_shape_manual(values = seq_len(length(df_mean$simulation))) +
  scale_fill_mpimg(name = "mpi_extend") +
  scale_color_manual(
    values = list(
      "zeisel" = "#60636a",
      "pbmc3k" = "#a5acaf"
    )
  ) +
  theme_bw(base_size = 20) +
  theme(
    axis.text.x = element_text(
      color = "black",
      angle = 45,
      vjust = 1,
      hjust = 1
    ),
    text = element_text(size = 20),
  ) +
  guides(fill = "none")

# p_mean_ari_bicl

ggsave(
  plot = p_mean_ari_bicl,
  filename = file.path(imgdir, "bicl_mean_ARI_cells.pdf"),
  width = 2500,
  height = 1650,
  units = "px"
)
ggsave(
  plot = p_mean_ari_bicl,
  filename = file.path(imgdir, "bicl_mean_ARI_cells.png"),
  width = 2500,
  height = 1650,
  units = "px"
)
```

```{r}
p_mean_ce_bicl <- df_mean %>%
  ggplot(aes(
    x = algorithm,
    y = mean_CE
  )) +
  geom_boxplot(
    aes(fill = algorithm),
    color = "#383e42",
    alpha = 1,
    outlier.alpha = 0
  ) +
  geom_jitter(
    aes(
      x = algorithm,
      y = mean_CE,
      color = dataset,
      group = dataset,
      shape = simulation
    ),
    stroke = 1.5,
    size = 2,
    width = 0.2
  ) +
  labs(
    title = "Mean CE",
    y = "mean CE",
    x = "algorithm"
  ) +
  scale_shape_manual(values = seq_len(length(df_mean$simulation))) +
  scale_fill_mpimg(name = "mpi_extend") +
  scale_color_manual(
    values = list(
      "zeisel" = "#60636a",
      "pbmc3k" = "#a5acaf"
    )
  ) +
  theme_bw(base_size = 18) +
  theme(
    axis.text.x = element_text(
      color = "black",
      angle = 45,
      vjust = 1,
      hjust = 1
    ),
    text = element_text(size = 20),
  ) +
  guides(fill = "none")

# p_mean_ce_bicl

ggsave(
  plot = p_mean_ce_bicl,
  filename = file.path(imgdir, "bicl_mean_CE.pdf"),
  width = 2500,
  height = 1650,
  units = "px"
)
ggsave(
  plot = p_mean_ce_bicl,
  filename = file.path(imgdir, "bicl_mean_CE.png"),
  width = 2500,
  height = 1650,
  units = "px"
)
```

# Gene evaluation

## max ARI
```{r}
p_max_ari_g_bicl <- df_max %>%
  ggplot(aes(
    x = algorithm,
    y = max_ARI_genes
  )) +
  geom_boxplot(
    aes(fill = algorithm),
    color = "#383e42",
    alpha = 1,
    outlier.alpha = 0
  ) +
  geom_jitter(
    aes(
      x = algorithm,
      y = max_ARI_genes,
      color = dataset,
      group = dataset,
      shape = simulation
    ),
    stroke = 1.5,
    size = 2,
    width = 0.2
  ) +
  labs(
    title = "Max ARI genes",
    y = "max ARI",
    x = "algorithm"
  ) +
  scale_shape_manual(values = seq_len(length(df_max$simulation))) +
  scale_fill_mpimg(name = "mpi_extend") +
  scale_color_manual(
    values = list(
      "zeisel" = "#60636a",
      "pbmc3k" = "#a5acaf"
    )
  ) +
  theme_bw(base_size = 18) +
  theme(
    axis.text.x = element_text(
      color = "black",
      angle = 45,
      vjust = 1,
      hjust = 1
    ),
    text = element_text(size = 20),
  ) +
  guides(fill = "none")

# p_max_ari_g_bicl

ggsave(
  plot = p_max_ari_g_bicl,
  filename = file.path(imgdir, "bicl_max_ARI_genes.pdf"),
  width = 2500,
  height = 1650,
  units = "px"
)

ggsave(
  plot = p_max_ari_g_bicl,
  filename = file.path(imgdir, "bicl_max_ARI_genes.png"),
  width = 2500,
  height = 1650,
  units = "px"
)
```

```{r}
p_mean_ari_g_bicl <- df_mean %>%
  ggplot(aes(
    x = algorithm,
    y = mean_ARI_genes
  )) +
  geom_boxplot(
    aes(fill = algorithm),
    color = "#383e42",
    alpha = 1,
    outlier.alpha = 0
  ) +
  geom_jitter(
    aes(
      x = algorithm,
      y = mean_ARI_genes,
      color = dataset,
      group = dataset,
      shape = simulation
    ),
    stroke = 1.5,
    size = 2,
    width = 0.2
  ) +
  labs(
    title = "Mean ARI genes",
    y = "Mean ARI",
    x = "algorithm"
  ) +
  scale_shape_manual(values = seq_len(length(df_mean$simulation))) +
  scale_fill_mpimg(name = "mpi_extend") +
  scale_color_manual(
    values = list(
      "zeisel" = "#60636a",
      "pbmc3k" = "#a5acaf"
    )
  ) +
  theme_bw(base_size = 18) +
  theme(
    axis.text.x = element_text(
      color = "black",
      angle = 45,
      vjust = 1,
      hjust = 1
    ),
    text = element_text(size = 20),
  ) +
  guides(fill = "none")

# p_mean_ari_g_bicl

ggsave(
  plot = p_mean_ari_g_bicl,
  filename = file.path(imgdir, "bicl_mean_ARI_genes.pdf"),
  width = 2500,
  height = 1650,
  units = "px"
)

ggsave(
  plot = p_mean_ari_g_bicl,
  filename = file.path(imgdir, "bicl_mean_ARI_genes.png"),
  width = 2500,
  height = 1650,
  units = "px"
)

ggsave(
  plot = p_mean_ari_g_bicl,
  filename = file.path(imgdir, "bicl_mean_ARI_genes.tiff"),
  width = 2500,
  height = 1650,
  units = "px"
)
```


# Figure panels

```{r}
fig <- (p_max_ce_bicl + p_max_ari_g_bicl + p_mean_ce_bicl + p_mean_ari_g_bicl) +
  plot_layout(guides = "collect") +
  scale_shape_manual(values = seq_len(length(df_all$simulation))) +
  scale_fill_mpimg(name = "mpi_extend") +
  scale_color_manual(
    values = list(
      "zeisel" = "#60636a",
      "pbmc3k" = "#a5acaf"
    )
  ) +
  plot_annotation(tag_levels = "a")

ggsave(
  plot = fig,
  filename = file.path(imgdir, "bicl_panel.pdf"),
  width = 3800,
  height = 3200,
  units = "px"
)

ggsave(
  plot = fig,
  filename = file.path(imgdir, "bicl_panel.png"),
  width = 3800,
  height = 3200,
  units = "px"
)

ggsave(
  plot = fig,
  filename = file.path(imgdir, "bicl_panel.tiff"),
  width = 3800,
  height = 3200,
  units = "px"
)
```


# Panels

## Review Panel
```{r}
fig1 <- (p_max_ari + p_mean_ari + plot_layout(guides = "collect")) +
  plot_annotation(tag_levels = "a") &
  theme(
    text = element_text(size = 18),
    plot.title = element_text(size = 18, face = "plain"),
    plot.tag = element_text(size = 20, face = "bold"),
    legend.text = element_text(size = 14)
  )
# theme(
#   text = element_text(size = 20),
#   plot.title = element_text(size = 22, face = "plain"),
#   plot.tag = element_text(size = 22, face = "bold")
# )

ggsave(
  plot = fig1,
  filename = file.path(imgdir, "upd_bench_review_panel.pdf"),
  width = 6400,
  height = 2200,
  units = "px"
)

ggsave(
  plot = fig1,
  filename = file.path(imgdir, "upd_bench_review_panel.png"),
  width = 6400,
  height = 2200,
  units = "px"
)

ggsave(
  plot = fig1,
  filename = file.path(imgdir, "upd_bench_review_panel.tiff"),
  width = 6400,
  height = 2200,
  units = "px"
)
```

# Panel biclustering & cell clustering combined

```{r}
bicl_cc <- (p_max_ari + p_mean_ari + plot_layout(guides = "collect")) /
  (p_max_ce_bicl + p_mean_ce_bicl + plot_layout(guides = "collect")) +
  plot_annotation(tag_levels = "a") &
  theme(
    text = element_text(size = 18),
    plot.title = element_text(size = 24, face = "plain"),
    plot.tag = element_text(size = 20, face = "bold"),
    legend.text = element_text(size = 18),
    axis.text.x = element_text(size = 18),
    axis.text.y = element_text(size = 18)
  )

# bicl_cc

ggsave(
  plot = bicl_cc,
  filename = file.path(imgdir, "bicl_and_cell_cl_sparse.pdf"),
  width = 6400,
  height = 4400,
  units = "px"
)

ggsave(
  plot = bicl_cc,
  filename = file.path(imgdir, "bicl_and_cell_cl_sparse.png"),
  width = 6400,
  height = 4400,
  units = "px"
)

ggsave(
  plot = bicl_cc,
  filename = file.path(imgdir, "bicl_and_cell_cl_sparse.tiff"),
  width = 6400,
  height = 4400,
  units = "px"
)
```

# Log-distribution

```{r}
library(splatter)
library(SingleCellExperiment)
library(scater)
library(scuttle)
library(scran)
library(scRNAseq)
library(TENxPBMCData)
library(Seurat)
```


```{r}
zce <- ZeiselBrainData()
clust.sce <- quickCluster(zce)
zce <- computeSumFactors(zce, cluster = clust.sce, min.mean = 0.1)
zce <- logNormCounts(zce)
zce <- runUMAP(zce)
counts(zce) <- as.matrix(counts(zce))
logcounts(zce) <- as.matrix(logcounts(zce))
```

```{r}
pce <- TENxPBMCData(dataset = "pbmc3k")
rownames(pce) <- make.names(rowData(pce)$Symbol_TENx, unique = TRUE)
colnames(pce) <- colData(pce)$Barcode

# For pre-processing we used Seurat.
pbmc <- CreateSeuratObject(
  counts = as.matrix(counts(pce)),
  assay = "RNA",
  project = "pbmc3k",
  min.cells = 3,
  min.features = 200,
  meta.data = as.data.frame(colData(pce))
)

pbmc[["percent.mt"]] <- PercentageFeatureSet(pbmc, pattern = "^MT-")

# Filter data
pbmc <- subset(
  pbmc,
  subset = nFeature_RNA > 200 & nFeature_RNA < 2500 & percent.mt < 5
)
no_zeros_rows <- rowSums(pbmc, slot = "counts") > 0
pbmc <- pbmc[no_zeros_rows, ]

# Normalization
pbmc <- NormalizeData(
  pbmc,
  normalization.method = "LogNormalize",
  scale.factor = 10000,
  verbose = FALSE
)

pbmc <- FindVariableFeatures(pbmc, nfeatures = 2000, verbose = FALSE)

# Scaling
all.genes <- rownames(pbmc)
pbmc <- ScaleData(pbmc, features = all.genes, verbose = FALSE)

# Run PCA
pbmc <- RunPCA(
  pbmc,
  features = VariableFeatures(object = pbmc),
  verbose = FALSE
)

# Cell clustering
pbmc <- FindNeighbors(pbmc, dims = 1:10, verbose = FALSE)
pbmc <- FindClusters(pbmc, resolution = 0.5, verbose = FALSE)

pbmc <- RunUMAP(pbmc, dims = 1:10, verbose = FALSE)
# DimPlot(pbmc, reduction = "umap", label = FALSE, pt.size = 0.5)

new.cluster.ids <- c(
  "naive_CD4_Tcell",
  "CD14_monocyte",
  "memory_CD4_Tcell",
  "Bcell",
  "CD8_Tcell",
  "FCGR3A_monocyte",
  "NKcell",
  "DC",
  "platelet"
)

names(new.cluster.ids) <- levels(pbmc)
pbmc <- RenameIdents(pbmc, new.cluster.ids)
pbmc$cell_type <- Idents(pbmc)

pce <- as.SingleCellExperiment(pbmc)
logcounts(pce) <- as.matrix(logcounts(pce))
counts(pce) <- as.matrix(counts(pce))
```

```{r}
zeisel_params <- splatEstimate(zce)
```

```{r}
pbmc_params <- splatEstimate(pce)
```

```{r}
pnts <- seq(0, 500, by = 0.01)

splat_log <- function(x, xz, k) 1 / (1 + exp(-k * (x - xz)))

log_pnts <- splat_log(
  x = pnts,
  xz = 20,
  k = -0.05
)

df <- data.frame(exprs = pnts, prob = log_pnts)
log_prob <- ggplot(df, aes(x = exprs, y = prob)) +
  geom_line() +
  xlim(x = c(0, 200)) +
  ggtitle("Dropout Probability - Sparse Data") +
  labs(x = "Expression", y = "Probability") +
  theme_bw()
```

```{r}
zeisel_log_pnts <- splat_log(
  x = pnts,
  xz = zeisel_params@dropout.mid,
  k = zeisel_params@dropout.shape
)

df <- data.frame(exprs = pnts, prob = zeisel_log_pnts)
zeisel_log_prob <- ggplot(df, aes(x = exprs, y = prob)) +
  geom_line() +
  xlim(x = c(0, 200)) +
  ggtitle("Dropout Probability - Zeisel") +
  labs(x = "Expression", y = "Probability") +
  theme_bw()
```


```{r}
pbmc_log_pnts <- splat_log(
  x = pnts,
  xz = pbmc_params@dropout.mid,
  k = pbmc_params@dropout.shape
)

df <- data.frame(exprs = pnts, prob = pbmc_log_pnts)
pbmc_log_prob <- ggplot(df, aes(x = exprs, y = prob)) +
  geom_line() +
  xlim(x = c(0, 200)) +
  ggtitle("Dropout Probability - PBMC3k") +
  labs(x = "Expression", y = "Probability") +
  theme_bw()
```

```{r}
dropouts <- log_prob +
  zeisel_log_prob +
  pbmc_log_prob +
  plot_annotation(tag_levels = "a") &
  theme(
    text = element_text(size = 18),
    plot.title = element_text(size = 18, face = "plain"),
    plot.tag = element_text(size = 20, face = "bold"),
    legend.text = element_text(size = 14)
  )

# dropouts
ggsave(
  plot = dropouts,
  filename = file.path(imgdir, "dropout_probs.pdf"),
  width = 6400,
  height = 2200,
  units = "px"
)

ggsave(
  plot = dropouts,
  filename = file.path(imgdir, "dropout_probs.png"),
  width = 6400,
  height = 2200,
  units = "px"
)

ggsave(
  plot = dropouts,
  filename = file.path(imgdir, "dropout_probs.tiff"),
  width = 6400,
  height = 2200,
  units = "px"
)
```

# Sparsity
```{r}
csv_dir <- file.path("./data/sim/raw_sparse/zeisel")
zeisel_dirs <- list.dirs(csv_dir, full.names = TRUE)
zeisel_csvs <- list.files(
  zeisel_dirs,
  pattern = "sparsity.csv",
  full.names = TRUE
)

csv_dir <- file.path("./data/sim/raw_sparse/pbmc3k")
pbmc3k_dirs <- list.dirs(csv_dir)
pbmc3k_csvs <- list.files(
  pbmc3k_dirs,
  pattern = "sparsity.csv",
  full.names = TRUE
)

zdf <- list()
pdf <- list()

for (i in seq_len(length(zeisel_csvs))) {
  f <- zeisel_csvs[i]
  zdf[[i]] <- readr::read_csv(f)
}

for (i in seq_len(length(pbmc3k_csvs))) {
  f <- pbmc3k_csvs[i]
  pdf[[i]] <- readr::read_csv(f)
}

zdf <- do.call("rbind", zdf)
pdf <- do.call("rbind", pdf)

mean(zdf$original)
mean(zdf$sparse)

mean(pdf$original)
mean(pdf$sparse)
```                       

# Environment

```{r}
sessionInfo()
```

