---
jupyter:
  jupytext:
    formats: 'ipynb,qmd'
    text_representation:
      extension: .qmd
      format_name: quarto
      format_version: '1.0'
      jupytext_version: 1.16.1
  kernelspec:
    display_name: R 4.4
    language: R
    name: ir44
---

# Setup
```{r}
renv::load("/project/kohl_analysis/analysis/CAdir")
devtools::load_all("/home/kohl/PhD/gits/ClemensKohl/CAdir")
# source("./utils.R")

suppressPackageStartupMessages({
  library(dplyr)
  library(tidyr)
  library(readr)
  library(ggplot2)
  library(ggthemes)
})

dir <- "/project/kohl_analysis/analysis/CAdir/results/results/"
imgdir <- file.path(dir, "img/figure3/")

setwd(dir)
dir.create(imgdir, recursive = TRUE)

options(repr.plot.width = 20, repr.plot.height = 15)
```

# Cell clustering benchmarking

```{r}
date <- "20240620"
base_dir <- file.path("/project/kohl_data/CAdir/benchmarking/results/simulated", date)
indir = file.path(base_dir, "eval")

```


## simulated data

Benchmarking results based on Zeisel Brain data:
```{r}
zeisel_eval <- readRDS(
  file.path(indir,
  paste0(date, "_zeisel_collated.rds")
  ))

dfz <- zeisel_eval %>%
    mutate(dataset = "zeisel") %>%
    mutate(simulation = paste(dePROB, defacLOC, defacSCALE, sep="_")) %>%
    mutate(simulation = factor(simulation, levels = c('0.02_0.75_0.75',
                                                      '0.06_0.75_0.75',
                                                      '0.1_0.75_0.75',
                                                      '0.02_1.5_1.5',
                                                      '0.06_1.5_1.5',
                                                      '0.1_1.5_1.5')))

table(zeisel_eval$algorithm,
      paste(zeisel_eval$dePROB, zeisel_eval$defacLOC, zeisel_eval$defacSCALE, sep="_"))

```

Benchmarking results based on PBMC3k data:
```{r}
pbmc_eval <- readRDS(
  file.path(indir,
  paste0(date, "_pbmc3k_collated.rds")
  ))

dfp <- pbmc_eval %>%
    mutate(dataset = "pbmc3k") %>%
    mutate(simulation = paste(dePROB, defacLOC, defacSCALE, sep="_")) %>%
    mutate(simulation = factor(simulation, levels = c('0.02_0.75_0.75',
                                                      '0.06_0.75_0.75',
                                                      '0.1_0.75_0.75',
                                                      '0.02_1.5_1.5',
                                                      '0.06_1.5_1.5',
                                                      '0.1_1.5_1.5')))

table(pbmc_eval$algorithm,
      paste(pbmc_eval$dePROB, pbmc_eval$defacLOC, pbmc_eval$defacSCALE, sep="_"))
```

Combining the benchmarking resuls:
```{r}
df_all <- rbind(dfz, dfp)

df_all$algorithm <- gsub("CAbiNet_igraph", "CAbiNet", df_all$algorithm)

df_all$algorithm <- factor(df_all$algorithm, levels =
                           c("CAdir",
                             "kmeans",
                             "CAbiNet",
                             "RaceID",
                             "RaceID_auto",
                             "Seurat",
                             "Monocle3",
                             "SC3",
                             "SIMLR"))


df <- df_all %>% group_by(simulation, algorithm, dataset) %>%
        mutate(mean_ARI = mean(ARI, na.rm = TRUE)) %>%
        mutate(mean_NMI = mean(NMI, na.rm = TRUE)) %>%
        select(dataset, simulation, algorithm, mean_ARI, mean_NMI) %>%
        distinct() %>%
        ungroup()
```

### Simulated data benchmarking - Max Results
```{r}
df <- df_all %>%
    group_by(simulation, algorithm, dataset) %>%
    mutate(max_ARI = max(ARI, na.rm = TRUE)) %>%
    mutate(max_NMI = max(NMI, na.rm = TRUE)) %>%
    select(dataset, simulation, algorithm, max_ARI, max_NMI) %>%
    distinct() %>%
    ungroup()

df$max_ARI[is.infinite(df$max_ARI)] <- 0
df$max_NMI[is.infinite(df$max_NMI)] <- 0

```

```{r}
p <- df %>%
ggplot(aes(x=algorithm,
           y=max_ARI)) +
    geom_boxplot(aes(fill = algorithm),
                 color = "#383e42",
                 alpha = 1,
                 outlier.alpha = 0)+
    geom_jitter(aes(x=algorithm,
                    y=max_ARI,
                    color = dataset,
                    group = dataset,
                    shape = simulation),
                    stroke =1.5,
                    size = 2,
                    width = 0.2) +
    labs(title = "max ARI cells on simulated data",
         y = "max ARI cells",
         x = "algorithm") +
    scale_shape_manual(values = seq_len(length(df$simulation))) +
    # ggthemes::scale_fill_tableau(palette = "Tableau 20",
    #                           type = "regular",
    #                           direction = 1)+
    scale_fill_mpimg(name = "mpi_extend") +
    scale_color_manual(values = list("zeisel" = "#60636a", "pbmc3k" = "#a5acaf")) +
    theme_bw(base_size = 16) +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
    guides(fill = "none")

p

ggsave(plot = p,
       filename = file.path(imgdir, "sim_bench_max_ARI_cells.pdf"),
       width = 3000,
       height = 2000,
       units = "px")
```

```{r}
p <- df %>%
ggplot(aes(x=algorithm,
           y=max_NMI)) +
    geom_boxplot(aes(fill = algorithm),
                 color = "#383e42",
                 alpha = 1,
                 outlier.alpha = 0)+
    geom_jitter(aes(x=algorithm,
                    y=max_NMI,
                    color = dataset,
                    group = dataset,
                    shape = simulation),
                    stroke =1.5,
                    size = 2,
                    width = 0.2) +
    labs(title = "max NMI on simulated data",
         y = "max NMI",
         x = "algorithm") +
    scale_shape_manual(values = seq_len(length(df$simulation))) +
    ggthemes::scale_fill_tableau(palette = "Tableau 20",
                              type = "regular",
                              direction = 1)+
    scale_color_manual(values = list("zeisel" = "#60636a", "pbmc3k" = "#a5acaf")) +
    theme_bw(base_size = 16) +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
    guides(fill = "none")

p

ggsave(plot = p,
       filename = file.path(imgdir, "sim_bench_max_NMI_cells.pdf"),
       width = 3000,
       height = 2000,
       units = "px")
```


### Simulated data benchmarking - Average Results
```{r}
df <- df_all %>% group_by(simulation, algorithm, dataset) %>%
        mutate(mean_ARI = mean(ARI, na.rm = TRUE)) %>%
        mutate(mean_NMI = mean(NMI, na.rm = TRUE)) %>%
        select(dataset, simulation, algorithm, mean_ARI, mean_NMI) %>%
        distinct() %>%
        ungroup()

```



```{r}
p <- df %>%
ggplot(aes(x=algorithm,
           y=mean_ARI)) +
    geom_boxplot(aes(fill = algorithm),
                 color = "#383e42",
                 alpha = 1,
                 outlier.alpha = 0)+
    geom_jitter(aes(x=algorithm,
                    y=mean_ARI,
                    color = dataset,
                    group = dataset,
                    shape = simulation),
                    stroke =1.5,
                    size = 2,
                    width = 0.2) +
    labs(title = "Mean ARI cells",
         y = "mean ARI",
         x = "algorithm") +
    scale_shape_manual(values = seq_len(length(df$simulation))) +
    ggthemes::scale_fill_tableau(palette = "Tableau 20",
                              type = "regular",
                              direction = 1)+
    scale_color_manual(values = list("zeisel" = "#60636a", "pbmc3k" = "#a5acaf")) +
    theme_bw(base_size = 16) +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
    guides(fill = "none")

p


ggsave(plot = p,
       filename = file.path(imgdir, "sim_bench_mean_ARI_cells.pdf"),
       width = 2500,
       height = 1650,
       units = "px")
```

```{r}
p <- df %>%
ggplot(aes(x=algorithm,
           y=mean_NMI)) +
    geom_boxplot(aes(fill = algorithm),
                 color = "#383e42",
                 alpha = 1,
                 outlier.alpha = 0)+
    geom_jitter(aes(x=algorithm,
                    y=mean_NMI,
                    color = dataset,
                    group = dataset,
                    shape = simulation),
                    stroke =1.5,
                    size = 2,
                    width = 0.2) +
    labs(title = "mean NMI on simulated data",
         y = "mean NMI",
         x = "algorithm") +
    scale_shape_manual(values = seq_len(length(df$simulation))) +
    ggthemes::scale_fill_tableau(palette = "Tableau 20",
                              type = "regular",
                              direction = 1)+
    scale_color_manual(values = list("zeisel" = "#60636a", "pbmc3k" = "#a5acaf")) +
    theme_bw(base_size = 16) +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
    guides(fill = "none")

p


ggsave(plot = p,
       filename = file.path(imgdir, "sim_bench_mean_NMI_cells.pdf"),
       width = 2500,
       height = 1650,
       units = "px")
```



## real data

```{r}
date <- "20240620"
evldir = file.path("/project/kohl_data/CAdir/benchmarking/results/real", date, "eval")

options(repr.plot.width = 15, repr.plot.height = 10)
```

```{r}
### Load the results of real data sets
files = list.files(evldir, '*.rds', full.names = TRUE)

df = data.frame()
for (file in files){

  data = readRDS(file)
  df = bind_rows(df, data)

}

df$dataset = gsub('_filtered', '', df$dataset)

### Simulated data sets

# simdf <- rbind(dfz, dfp)
simdf <- df_all
simdf$dataset = paste0(simdf$dataset, '_', simdf$simulation)

# simdf$dataset = paste(simdf$dataset, simdf$dePROB, simdf$defacLOC, simdf$defacSCALE, sep = '_')

commoncols = intersect(colnames(df), colnames(simdf))

### Merge two data frames
df <- rbind(df[,commoncols], simdf[, commoncols])
```

```{r}
df$dataset[df$dataset == 'PBMC_10X'] = 'PBMC10x'
df$dataset[df$dataset == "Tirosh_nonmaglignant"] = "Tirosh"
df$dataset[df$dataset == "ZeiselBrain"] = "Zeisel"
df$dataset[df$dataset == "dmel_E14-16h"] = "DmelSpatial"
df$dataset[df$dataset == "tabula_sapiens_tissue"] = 'TabulaSapiens'
df$dataset[df$dataset == "brain_organoids"] = "BrainOrganoids"

df <- df %>%
        mutate(algorithm = gsub("CAbiNet_igraph", "CAbiNet", algorithm)) %>%
        mutate(pattern = paste0(algorithm, dataset))
```

```{r}
# Filter out combinations where all runs fail.
test <- df %>%
        group_by(dataset, algorithm) %>%
        mutate(fail.n = sum(is.na(ARI)), scsd.n = n()) %>%
        filter(fail.n == scsd.n | (scsd.n == 0))

## pick 1 algor./dataset combinaton of failed runs
df_na <- test %>%
        group_by(algorithm, dataset) %>%
        arrange(runtime) %>%
        select(-fail.n, -scsd.n) %>%
        top_n(n = 1, wt = runtime)

run_stat = table(df$algorithm, df$dataset)
run_stat
```

```{r}
# Find missing runs (no values because crash/error)

# Find row and column indices of cells equal to 0
zero_indices <- which(run_stat == 0, arr.ind = TRUE)

# Create a data frame with row names and column names
zero_df <- data.frame(
  algorithm = rownames(run_stat)[zero_indices[, 1]],
  dataset = colnames(run_stat)[zero_indices[, 2]]
)

df_na = dplyr::bind_rows(df_na, zero_df)

```

```{r}
# Filter out runs which failed
subdf = df[!(df$pattern %in% test$pattern), ]
subdf = subdf[!is.na(subdf$ARI),]
subdf = rbind(subdf, df_na) # add a single instance of failed runs & missing runs.

subdf$algorithm = factor(subdf$algorithm, levels = c(
    "CAdir",
    "kmeans",
    "CAbiNet",
    "RaceID",
    "RaceID_auto",
    "Seurat",
    "Monocle3",
    "SC3",
    "SIMLR"
))

df_g <- subdf %>%
    group_by(algorithm, dataset) %>%
    mutate(Mean_ARI = mean(ARI),
           Max_ARI = max(ARI),
           Median_ARI = median(ARI),
           Mean_NMI = mean(NMI),
           Max_NMI = max(NMI))

df_g$dataset = factor(df_g$dataset, levels = c(
    "Darmanis",
    "FreytagGold",
    "PBMC10x",
    "Tirosh",
    "Zeisel",
    "BaronPancreas",
    "DmelSpatial",
    "TabulaSapiens",
    "BrainOrganoids",
    unique(simdf$dataset)
))
```

```{r}
df_m <- df_g %>%
    group_by(sim, algorithm, dataset) %>%
    mutate(max_NMI = max(NMI, na.rm = TRUE)) %>%
    mutate(max_ARI = max(ARI, na.rm = TRUE)) %>%
    select(dataset, sim, algorithm, max_NMI, max_ARI) %>%
    distinct() %>%
    ungroup()

df_m$max_NMI[is.infinite(df_m$max_NMI)] <- NA
df_m$max_ARI[is.infinite(df_m$max_ARI)] <- NA
```

```{r}
options(repr.plot.width=10, repr.plot.height=5)

# Remove simulated data sets
df_real <- df_g %>% filter(dataset %in% c("Darmanis",
                                          "FreytagGold",
                                          "PBMC10x",
                                          "Tirosh",
                                          "Zeisel",
                                          "BaronPancreas",
                                          "DmelSpatial",
                                          "TabulaSapiens",
                                          "BrainOrganoids") )
df_real$dataset = droplevels(df_real$dataset)
df_real <- df_real %>%
    drop_na(algorithm) %>%
    droplevels()

na_txt <- df_real[is.na(df_real$Max_ARI), ]
na_txt$NAs <- as.character("N/A")
```

```{r}

# library(gguidance)
p <- ggplot(df_real, aes(x = algorithm, y = dataset, fill = Max_ARI)) +
  geom_tile() +
  geom_text(
    aes(label = round(Max_ARI, 2)),
    color = "white",
    size = 3,
    check_overlap = T
  ) +
  geom_text(
    data = na_txt,
    aes(x = algorithm, y = dataset, label = NAs),
    color = "white",
    size = 3,
    check_overlap = T
  ) +
  scale_fill_gradientn(
    colours = c("#29485d", "#006c66", "#c6d325", "#ef7c00"),
    limits = c(0, 1),
    # oob = scales::squish,
    # guide = "colourbar_custom"
    na.value="#777777",
    name = "Max ARI"
  ) + 
  theme_minimal() +
  theme(panel.border = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    axis.text.y = element_text(color = "black"),
    axis.text.x = element_text(angle = 30, hjust = 1, color = "black"),
    text = element_text(size = 16),
    plot.title = element_text(size = 16, face = "plain")) +
  labs(x = 'Dataset', y = 'Algorithm', title = "Maximal ARI on experimental data")

p
ggsave(plot = p,
       filename = file.path(imgdir, "real_bench_max_ARI_cells.pdf"),
        width = 2000,
        height = 1750,
       units = "px")

```




## Calculate % successful runs

```{r}
n_param <- 108

stats <- df %>%
group_by(algorithm, dataset) %>%
mutate(n_runs = n(),
       NA_ARI = sum(is.na(ARI)),
       NA_NMI = sum(is.na(NMI))) %>%
mutate(perc_ARI_succ = round((n_runs - NA_ARI) / n_param, 2),
       perc_NMI_succ = round((n_runs - NA_NMI) / n_param, 2),
       perc_ARI_NA = round(NA_ARI / n_param, 2),
       perc_NMI_NA = round(NA_NMI / n_param, 2),
       perc_crash = round((n_param - n_runs) / n_param, 2)) %>%
select(algorithm, dataset, perc_ARI_succ, perc_NMI_succ, perc_ARI_NA, perc_NMI_NA, perc_crash) %>%
distinct()

```

```{r}
stats$algorithm = factor(stats$algorithm, levels = c(
    "CAdir",
    "kmeans",
    "CAbiNet",
    "RaceID",
    "RaceID_auto",
    "Seurat",
    "Monocle3",
    "SC3",
    "SIMLR"
))

stats$dataset = factor(stats$dataset, levels = c("Darmanis",
                                                 "FreytagGold",
                                                 "PBMC10x",
                                                 "Tirosh",
                                                 "Zeisel",
                                                 "BaronPancreas",
                                                 "DmelSpatial",
                                                 "TabulaSapiens",
                                                 "BrainOrganoids",
                                                 unique(simdf$dataset)))

```

```{r}
all_comb <- crossing(algorithm = stats$algorithm, dataset = stats$dataset) %>%
    mutate(comb = paste0(algorithm, "_", dataset))

comb_in_data <- stats %>%
    mutate(comb = paste0(algorithm, "_", dataset)) %>%
    pull(comb)

not_in_data <- which(!all_comb$comb %in% comb_in_data)

missing_comb <- all_comb[not_in_data, ]
missing_comb <- missing_comb %>%
    select(algorithm, dataset) %>%
    mutate(perc_ARI_succ = 0,
           perc_NMI_succ = 0,
           perc_ARI_NA = 0,
           perc_NMI_NA = 0,
           perc_crash = 1)

stats <- bind_rows(stats, missing_comb)
```

```{r}
p <- stats %>%
    distinct() %>%
    select(-perc_NMI_succ, -perc_NMI_NA) %>%
    pivot_longer(cols = starts_with("perc"), names_to = "stat", values_to = "perc") %>%
    mutate(stat = factor(stat, levels = c("perc_ARI_succ", "perc_ARI_NA", "perc_crash"))) %>%
    ggplot(aes(x = 1, y = perc, fill = stat )) +
        geom_col(position = "fill") +
        facet_grid(algorithm ~ dataset, as.table = FALSE, switch = "both") +
        scale_y_continuous(expand = c(0, 0)) +
        scale_x_continuous(expand = c(0, 0)) +
        theme(panel.grid = element_blank(),
               axis.ticks = element_blank(),
               axis.text = element_blank(),
               strip.background = element_blank(),
               strip.text.x = element_text(angle = 30, hjust = 0.95, vjust = 0.9),
               strip.text.y.left = element_text(angle = 0, hjust = 0.95),
               strip.clip = "off",
               text = element_text(size=16)
               , panel.spacing = unit(1.5, "pt")
              ) +
        scale_fill_manual(values = c("perc_ARI_succ" = "#59A14F", "perc_ARI_NA" = "#F28E2B", "perc_crash" = "#E15759"),
                          name = "% runs",
                          labels = c("Success", "N/A", "Crashed") ) +
        ggtitle("Fraction of successful and failed runs - ARI") +
        xlab("Dataset") +
        ylab("Algorithm")

# ggsave(plot = p,
#        filename = file.path(outdir, "barplots_fraction_successful_runs_ARI.pdf"),
#        width = 11,
#        height = 6)

q <- p + theme(text = element_text(size = 11))

ggsave(plot = q,
       filename = file.path(imgdir, "barplots_fraction_successful_runs_ARI_wide.pdf"),
       width = 8, height = 4.2)
q
```






# Runtime & Scalability
```{r}
mpgGreen = "#006c66"
mpgDarkGreen = "#005555"
mpgDarkGrey = "#777777"
mpgGreenLight = "#c6d325"
mpgOrange = '#ef7c00'
mpgGrau = "#a7a7a8" # MPG-Grau
mpgDarkBlue = "#29485d" # MPG Dunkelblau
mpgLightBlue = "#00b1ea" # MPG Hellblau

eval_files = list.files(
  '/project/kohl_data/CAdir/benchmarking/results/scalability/20240515_institute_seminar/out',
  pattern = '*.csv',
  full.names = T
)


scal_df = data.frame()
for (f in eval_files){
    df = read_csv(f, progress = FALSE, show_col_types = FALSE)
    suppressWarnings({
      scal_df <- dplyr::bind_rows(scal_df, df)
  })
}

scal_df$dataset = gsub('_ngene-2000', '', scal_df$dataset)
scal_df$dataset = gsub('ncell-', '', scal_df$dataset)
scal_df$algorithm = gsub('CAbiNet_igraph', 'CAbiNet', scal_df$algorithm)

scal_df$algorithm <- factor(scal_df$algorithm, levels = c(
    'CAdir',
    'CAbiNet',
    'Monocle3',
    'RaceID',
    # 'RaceID_auto',
    'SC3',
    'SIMLR',
    'Seurat',
    'kmeans'
))

scal_df$dataset = as.numeric(scal_df$dataset)

scal_df <- scal_df[!is.na(scal_df$algorithm), ]

scal_df$total_runtime <- scal_df$runtime + ifelse(is.na(scal_df$runtime_dimreduc), yes = 0, no = scal_df$runtime_dimreduc)
table(scal_df$algorithm)
```

```{r}
options(repr.plot.width = 10, repr.plot.height = 10)

alph <- 0.6
rt <- ggplot(scal_df, aes(dataset,  (total_runtime/60))) +
geom_point(aes(group = algorithm, color = algorithm, alpha = algorithm), size = 2) +
geom_line(aes(group = algorithm, color = algorithm, alpha = algorithm, linetype = algorithm), linewidth = 1 )+
    scale_x_continuous(breaks = c( 1000,
                                  10000,
                                  20000,
                                  40000,
                                  60000,
                                  80000,
                                  100000,
                                  200000,
                                  400000,
                                  600000),
                       labels = c( '1000',
                                   '10000',
                                   '20000',
                                   '40000',
                                    '60000',
                                   '80000',
                                   '1e+05',
                                   '2e+05',
                                   '4e+05',
                                   '6e+05'
                                  )) +
labs(x = 'Number of cells', y = 'Running time (min)', title = "Runtime vs Data Set Size") +
coord_trans(x="log10") +
scale_alpha_manual(values = c(
    'CAdir' = 1,
    'CAbiNet' = alph,
    'Monocle3' = alph,
    'RaceID' = alph,
    # 'RaceID_auto' = alph,
    'SC3' = alph,
    'SIMLR' = alph,
    'Seurat' = alph,
    'kmeans' = alph
)) +
scale_colour_manual(values = c(
    'CAdir' = mpgOrange,
    'CAbiNet' = mpgDarkGreen,
    'Monocle3' = mpgDarkBlue,
    'RaceID' = mpgGrau,
    # 'RaceID_auto' = alph,
    'SC3' = mpgLightBlue,
    'SIMLR' = mpgGrau,
    'Seurat' = mpgGreenLight,
    'kmeans' = mpgGreen
)) +
# ggthemes::scale_colour_tableau() +
# ggthemes::scale_fill_tableau(palette = "Tableau 10",
#                               type = "regular",
#                               direction = 1)+
scale_linetype_manual(values = c(
    'CAdir' = "solid",
    'CAbiNet' = "solid",
    'Monocle3' = "solid",
    'RaceID' = "solid",
    # 'RaceID_auto' = "solid",
    'SC3' = "dashed",
    'SIMLR' = "solid",
    'Seurat' = "solid",
    'kmeans' = "solid"
  )) +
theme_bw(base_size = 18) +
theme(axis.text.x = element_text(angle = 30, vjust = 1, hjust=1))

rt

ggsave(
  plot = rt,
  filename = file.path(imgdir, "runtime_singleproc.pdf"),
  width = 2400,
  height = 2100,
  units = "px"
)
```



# Detection of cluster number

```{r}
indir <- "/project/kohl_data/CAdir/benchmarking/results/ct_detection"
res <- read_csv(file.path(indir, "240705_ct_detection.csv"),
  show_col_types = FALSE,
  progress = FALSE)

res <- res %>%
  mutate(diff_abs = cts_found-nr_cts) %>%
  mutate(diff_perc = cts_found/nr_cts) %>%
  mutate(log2diff = log2(cts_found/nr_cts)) %>%
  mutate(k = factor(k))
```

```{r}
log2diff <- ggplot(res, aes(x = nr_cts, y = log2diff, color = k)) +
  geom_point() +
  geom_line() +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "# clusters", y = "log2 diff", title = "Detected clusters") +
  scale_color_mpimg() +
  theme_bw(base_size = 18)

ggsave(
  filename = file.path(imgdir, "log2diff_ct_detection.pdf"),
  plot = log2diff,
  width = 1800,
  height = 1800,
  units = "px"
)
```



# Environment
```{r}
sessionInfo()
```


