---
title: Figure 3
jupyter:
  jupytext:
    formats: 'ipynb,qmd:quarto'
    text_representation:
      extension: .qmd
      format_name: quarto
      format_version: '1.0'
      jupytext_version: 1.16.1
  kernelspec:
    display_name: R 4.4.1
    language: R
    name: ir441
---

# Setup

```{r}
# Working directory should be the root directory of repository.
# setwd("./")
renv::load()
source("./results/utils.R")

suppressPackageStartupMessages({
  library(CAdir)
  library(APL)
  library(SingleCellExperiment)
  library(dplyr)
  library(tidyr)

  # To load the data set
  library(TENxPBMCData)
  library(Seurat)
  library(SeuratObject)
  library(scater)
  library(scuttle)
  library(scran)

  # Plotting
  library(ggsankey)
  # devtools::install_github("teunbrand/gguidance")
  library(gguidance)
  library(patchwork)
})

dir <- "./results/"
imgdir <- file.path(dir, "img/figure3/")
dir.create(imgdir, recursive = TRUE)

options(repr.plot.width = 20, repr.plot.height = 15)
```

## Load data

```{r}
sce <- sce_pbmc3k()
```

# CAdir

```{r}
set.seed(1234)

sce_bu <- sce
sce.dec <- scran::modelGeneVar(sce)
sce.top <- scran::getTopHVGs(sce.dec, prop = 0.2, var.threshold = NULL)
sce <- sce[sce.top, ]
sce <- runUMAP(sce, ntop = 2000)

ca <- cacomp(
  obj = as.matrix(logcounts(sce)),
  princ_coords = 3,
  dims = 30,
  top = nrow(sce),
  residuals = "pearson",
  python = TRUE,
  clip = TRUE
)
```

With `cutoff = NULL` CAdir tries to estimate the angle cutoff directly from the data.

## Split & Merge Clustering

```{r}
set.seed(2358)
cak <- dirclust_splitmerge(
  caobj = ca,
  k = 12,
  cutoff = NULL,
  method = "random",
  apl_quant = 0.99,
  counts = NULL,
  min_cells = 30,
  reps = NULL,
  make_plots = TRUE,
  apl_cutoff_reps = 100,
  qcutoff = 0.6,
  convergence_thr = 0.001
)

cak <- rank_genes(cadir = cak, caobj = ca)
top <- top_genes(cak)
```

### Annotate clusters

```{r}
cak <- annotate_biclustering(
  obj = cak,
  universe = rownames(sce),
  org = "hs"
)

cak <- rank_genes(cadir = cak, caobj = ca)
cak

sce$cadir <- cak@cell_clusters

um1 <- plotUMAP(sce, colour = "cadir")
um2 <- plotUMAP(sce, colour = "cell_type")

ari <- aricode::clustComp(sce$cadir, sce$cell_type)
p <- um1 + ggtitle(paste0("ARI: ", round(ari$ARI, 2))) + um2
p

ggsave(
  plot = p,
  file = file.path(imgdir, "umap.png"),
  width = 3600,
  height = 1800,
  units = "px"
)
```

## Association plots of clusters

```{r}
pc_mod_l <- plot_clusters_custom(
  cak,
  ca,
  show_genes = TRUE,
  label_genes = TRUE,
  ntop = 5,
  axis = TRUE,
  title_prefix = "",
  gsub_title = "_",
  outlier_cluster = "cluster_5",
  text_size = 19,
  return_list = TRUE
)

pc_mod <- ggpubr::ggarrange(
  plotlist = pc_mod_l,
  nrow = 2,
  ncol = 3
)

pc_mod

ggsave(
  plot = pc_mod,
  file = file.path(imgdir, "plot_clusters.pdf"),
  width = 3400,
  height = 2000,
  units = "px"
)

ggsave(
  plot = pc_mod,
  file = file.path(imgdir, "plot_clusters.png"),
  width = 3400,
  height = 2000,
  units = "px"
)
```

### Identify outlier genes & cells

```{r}
cak <- rank_genes(cak, ca)
rnks <- cak@gene_ranks$cluster_5
sce$cadir_mod <- gsub("_", " ", sce$cadir)
lvls <- gsub("_", " ", rownames(cak@directions))
sce$cadir_mod <- factor(sce$cadir_mod, levels = lvls)
p_expr <- scater::plotExpression(
  sce,
  features = head(rnks$Rowname, 4),
  x = "cadir_mod",
  colour_by = "cadir_mod",
  ncol = 2
) +
  scale_color_mpimg() +
  labs(x = "Cluster", title = "Top 4 genes cluster 5") +
  theme_bw(base_size = 18) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, color = "black"),
    legend.position = "none"
  )

p_expr

ggsave(
  plot = p_expr,
  file = file.path(imgdir, "cluster_5_top_genes.pdf"),
  width = 2200,
  height = 2000,
  units = "px"
)
ggsave(
  plot = p_expr,
  file = file.path(imgdir, "cluster_5_top_genes.png"),
  width = 2200,
  height = 2000,
  units = "px"
)
```

#### Correct outliers

```{r}
cell_rnk <- get_top_cells(cadir = cak, caobj = ca, cluster = "cluster_5")
top_cells <- cell_rnk$Colname[cell_rnk$Score >= 0]
head(cell_rnk)

rnks <- cak@gene_ranks$cluster_5
top_genes <- unique(rnks$Rowname[rnks$Score >= 0])
```

Cells that are strongly associated to the cluster:

```{r}
p_cl5_cells <- cluster_apl(
  ca,
  cak,
  cluster = "cluster_5",
  direction = cak@directions["cluster_5", ],
  group = which(cak@cell_clusters == "cluster_5"),
  highlight_cluster = TRUE,
  show_genes = TRUE,
  label_genes = FALSE,
  show_lines = FALSE,
  size_factor = 0.5,
  ntop = 5
) +
  ggrepel::geom_label_repel(
    data = cell_rnk[cell_rnk$Score >= 0, ],
    ggplot2::aes(
      x = x,
      y = y,
      label = Colname,
      text = NULL
    ),
    color = "#c6d325",
    box.padding = 1,
    max.overlaps = Inf
  )

p_cl5_cells

ggsave(
  plot = p_cl5_cells,
  file = file.path(imgdir, "cluster_5_cells.pdf"),
  width = 1600,
  height = 1600,
  units = "px"
)
ggsave(
  plot = p_cl5_cells,
  file = file.path(imgdir, "cluster_5_cells.png"),
  width = 1600,
  height = 1600,
  units = "px"
)
```

Remove outliers:

```{r}
sce_corr <- sce[
  (!rownames(sce) %in% top_genes),
  (!colnames(sce) %in% top_cells)
]

ca_corr <- cacomp(
  obj = as.matrix(logcounts(sce_corr)),
  princ_coords = 3,
  dims = 30,
  top = nrow(sce_corr),
  residuals = "pearson",
  python = TRUE,
  clip = TRUE
)

set.seed(2358)
cak_corr <- dirclust_splitmerge(
  caobj = ca_corr,
  k = 12,
  cutoff = NULL,
  method = "random",
  apl_quant = 0.99,
  counts = NULL,
  min_cells = 30,
  reps = 5,
  make_plots = FALSE,
  apl_cutoff_reps = 100,
  qcutoff = 0.6
)

cak_corr <- annotate_biclustering(
  obj = cak_corr,
  universe = rownames(sce_corr),
  org = "hs"
)

sce_corr$cadir_corr <- cak_corr@cell_clusters

cak_corr <- rank_genes(cadir = cak_corr, caobj = ca_corr)

pc_corr_list <- plot_clusters(
  cak_corr,
  ca_corr,
  show_genes = TRUE,
  label_genes = TRUE,
  axis = TRUE,
  ggncol = 2,
  ggnrow = 3,
  title_prefix = "",
  gsub_title = "_",
  text_size = 19,
  return_list = TRUE,
  legend_pos = "right"
)
pc_corr <- wrap_plots(pc_corr_list, ncol = 2, nrow = 3) +
  guide_area() +
  plot_layout(guides = "collect")

cak_corr
pc_corr

ggsave(
  plot = pc_corr,
  file = file.path(imgdir, "apl_clusters_corrected.pdf"),
  device = cairo_pdf,
  width = 3000,
  height = 2500,
  units = "px"
)
ggsave(
  plot = pc_corr,
  file = file.path(imgdir, "apl_clusters_corrected.png"),
  width = 3000,
  height = 2500,
  units = "px"
)
```

Sankey plot showing to which clusters the remaining cells from cluster 5 are being clustered.

```{r}
sce_corr$cadir2 <- cak_corr@cell_clusters
sce_sank <- sce_corr[, sce_corr$cadir == "cluster_5"]
cadir_cls <- unique(as.character(sce_sank$cadir))

data <- colData(sce_sank) %>%
  as.data.frame() %>%
  rename(
    "First" = "cadir",
    "Second" = "cadir2"
  )

df_cl <- data %>%
  make_long(First, Second)

info <- data.frame(
  Biclusters = as.factor(data$First),
  Truth = as.character(data$Second)
) %>%
  as_tibble() %>%
  group_by(Biclusters, Truth) %>%
  summarise(n = n()) %>%
  group_by(Truth) %>%
  mutate(Partition = n / sum(n)) %>%
  ungroup() %>%
  as.data.frame() %>%
  group_by(Truth) %>%
  filter(Partition == max(Partition)) %>%
  dplyr::select(Biclusters, Truth) %>%
  distinct(Biclusters, .keep_all = TRUE)


pal <- mpimg_pal()

c5cols <- pal(length(cadir_cls))
names(c5cols) <- cadir_cls

info <- left_join(
  data.frame("Biclusters" = names(c5cols), "col" = c5cols),
  info,
  by = "Biclusters"
)
info$col <- pal(nrow(info) + 1)[2:(nrow(info) + 1)]

c5cols <- c(c5cols, info$col)

names(c5cols) <- c(as.character(cadir_cls), info$Truth)


order <- c(
  "cluster_5",
  "Naive_CD4+_T_cell",
  "Natural_killer_cell",
  "Megakaryocyte",
  "B_cell"
)

df_cl$node <- gsub("_", " ", df_cl$node)
df_cl$next_node <- gsub("_", " ", df_cl$next_node)
names(c5cols) <- gsub("_", " ", names(c5cols))
order <- gsub("_", " ", order)


wrap <- 17
df_cl$node <- factor(
  stringr::str_wrap(df_cl$node, wrap),
  levels = stringr::str_wrap(order, wrap)
)
df_cl$next_node <- factor(
  stringr::str_wrap(df_cl$next_node, wrap),
  levels = stringr::str_wrap(order, wrap)
)

names(c5cols) <- stringr::str_wrap(names(c5cols), wrap)


sank <- ggplot(
  df_cl,
  aes(
    x = x,
    next_x = next_x,
    node = node,
    next_node = next_node,
    fill = node,
    label = as.character(node)
  )
) +
  geom_sankey(flow.alpha = 0.6, flow.fill = c("#777777")) +
  geom_sankey_label(size = 6) +
  labs(x = "") +
  scale_fill_manual(values = c5cols) +
  theme_sankey(base_size = 26) +
  theme(
    legend.position = "none"
  )

sank

ggsave(
  plot = sank,
  filename = file.path(imgdir, "sankey_plot_cluster_5.pdf"),
  device = cairo_pdf,
  width = 2700,
  height = 2000,
  units = "px"
)
ggsave(
  plot = sank,
  filename = file.path(imgdir, "sankey_plot_cluster_5.png"),
  device = cairo_pdf,
  width = 2700,
  height = 2000,
  units = "px"
)
```

### Platelet cells

```{r}
cak_corr_mod <- cak_corr

goa_res <- CAbiNet::per_cluster_goa(
  cabic = cak_corr_mod,
  universe = rownames(sce_corr),
  set = "CellMarker",
  org = "hs",
  min_size = 10,
  max_size = 500
)
head(goa_res$Megakaryocyte)
```

Top 5 most highly significant gene sets for cluster "Megakaryocyte":

```{r}
cl_goa <- goa_res$Megakaryocyte

p <- ggplot(
  cl_goa[1:5, ],
  aes(x = gene_set, y = -log10(padj), fill = -log10(padj))
) +
  geom_col() +
  scale_fill_gradientn(
    colours = c("#29485d", "#006c66", "#c6d325", "#ef7c00"),
  ) +
  theme_bw()
p
```

Gene Set enrichment over all corrected clusters:

```{r}
nclust <- length(goa_res)

goa_mat <- lapply(goa_res, function(x, nc = nclust) {
  subs <- min(nrow(x), nc)
  x[seq_len(subs), ]
})

goa_mat <- dplyr::bind_rows(goa_mat, .id = "cluster")

gr <- goa_mat[, c("cluster", "gene_set", "padj")]
gr <- complete(gr, cluster, gene_set, fill = list(padj = 1))
gr$gene_set <- gsub("_", " ", gr$gene_set)
gr$cluster <- gsub("_", " ", gr$cluster)

p_gs_enr <- ggplot(gr, aes(x = cluster, y = gene_set, fill = -log10(padj))) +
  geom_tile() +
  scale_fill_gradientn(
    colours = c("#29485d", "#006c66", "#c6d325", "#ef7c00"),
    limits = c(0, 30),
    # limits = c(0, quantile(-log10(gr$padj), 0.99)),
    oob = scales::squish,
    guide = "colourbar_custom"
  ) +
  coord_fixed() +
  theme_bw() +
  labs(
    x = "Cluster",
    y = "Gene Set",
    title = "Gene Set enrichment",
    fill = expression(atop("-log"[10], "\npadj"))
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, color = "black"),
    axis.text.y = element_text(color = "black"),
    text = element_text(size = 18),
    plot.title = element_text(size = 16, face = "plain")
  ) # "bold"

p_gs_enr

ggsave(
  plot = p_gs_enr,
  file = file.path(imgdir, "gene_set_enr_hm.pdf"),
  width = 2000,
  height = 3000,
  units = "px"
)
ggsave(
  plot = p_gs_enr,
  file = file.path(imgdir, "gene_set_enr_hm.png"),
  width = 2000,
  height = 3000,
  units = "px"
)
```

## Split & Merge plot

```{r}
sm <- sm_plot(
  cadir = cak,
  caobj = ca,
  rm_redund = TRUE,
  keep_end = TRUE,
  highlight_cluster = TRUE,
  show_genes = FALSE,
  annotate_clusters = TRUE,
  org = "hs"
)
sm

ggsave(
  plot = sm,
  file = file.path(imgdir, "split_merge_plot.pdf"),
  width = 3000,
  height = 1800,
  units = "px"
)
ggsave(
  plot = sm,
  file = file.path(imgdir, "split_merge_plot.png"),
  width = 3000,
  height = 1800,
  units = "px"
)
```

## Annotation - Sankey

```{r}
library(ggsankey)
sce_sank <- sce_corr

data <- colData(sce_sank) %>%
  as.data.frame() %>%
  rename('CAdir' = "cadir_corr", 'Annotation' = "cell_type")

df <- data %>%
  make_long(CAdir, Annotation)

info <- data.frame(
  Biclusters = as.factor(data$CAdir),
  Truth = as.character(data$Annotation)
) %>%
  as_tibble() %>%
  group_by(Biclusters, Truth) %>%
  summarise(n = n()) %>%
  group_by(Truth) %>%
  mutate(Partition = n / sum(n)) %>%
  ungroup() %>%
  as.data.frame() %>%
  group_by(Truth) %>%
  filter(Partition == max(Partition)) %>%
  dplyr::select(Biclusters, Truth) %>%
  distinct(Biclusters, .keep_all = TRUE)


pal <- mpi_extend_pal()

cols <- pal(length(unique(sce_sank$cadir)))
names(cols) <- unique(sce_sank$cadir)

info <- left_join(
  data.frame("Biclusters" = names(cols), "col" = cols),
  info,
  by = "Biclusters"
)

cols <- c(cols, info$col)

names(cols) <- c(as.character(unique(sce_sank$cadir)), info$Truth)

order <- c(
  "Naive_CD4+_T_cell",
  "Natural_killer_cell",
  "B_cell",
  "Monocyte",
  "Megakaryocyte",

  "0 - Naive CD4 T",
  "2 - Memory CD4 T",
  "4 - CD8 T",
  "6 - NK",
  "3 - B",
  "1 - CD14+ Mono",
  "5 - FCGR3A+ Mono",
  "7 - DC",
  "8 - Platelet"
)

df$node <- gsub("_", " ", df$node)
df$next_node <- gsub("_", " ", df$next_node)
names(cols) <- gsub("_", " ", names(cols))
order <- gsub("_", " ", order)

wrap <- 17
df$node <- factor(
  stringr::str_wrap(df$node, wrap),
  levels = stringr::str_wrap(order, wrap)
)
df$next_node <- factor(
  stringr::str_wrap(df$next_node, wrap),
  levels = stringr::str_wrap(order, wrap)
)

names(cols) <- stringr::str_wrap(names(cols), wrap)

sank_anno <- ggplot(
  df,
  aes(
    x = x,
    next_x = next_x,
    node = node,
    next_node = next_node,
    fill = node,
    label = as.character(node)
  )
) +
  geom_sankey(
    flow.alpha = 0.4,
  ) +
  geom_sankey_label(size = 6) +
  labs(x = "") +
  scale_fill_manual(values = cols) +
  theme_sankey(base_size = 26, base_family = "sans") +
  theme(
    legend.position = "none"
  )

sank_anno

ggsave(
  plot = sank_anno,
  filename = file.path(imgdir, "sankey_plot_corr_clustering.pdf"),
  width = 2700,
  height = 3200,
  device = cairo_pdf,
  units = "px"
)

ggsave(
  plot = sank_anno,
  filename = file.path(imgdir, "sankey_plot_corr_clustering.png"),
  width = 2700,
  height = 3200,
  units = "px"
)
```

# Figure panels

```{r}

sank <- ggplot(
  df_cl,
  aes(
    x = x,
    next_x = next_x,
    node = node,
    next_node = next_node,
    fill = node,
    label = as.character(node)
  )
) +
  geom_sankey(flow.alpha = 0.6, flow.fill = c("#777777")) +
  geom_sankey_label(size = 4) +
  labs(x = "") +
  scale_fill_manual(values = c5cols) +
  theme_sankey(base_size = 18, base_family = "sans") +
  theme(
    legend.position = "none"
  )


layout <- c(
  area(t = 1, l = 1, b = 6, r = 9),
  area(7, 1, 12, 5),
  area(7, 6, 12, 9),
  area(1, 10, 12, 12)
)

pcl_panel <- pc_mod_l
for (i in seq_len(length(pcl_panel))) {
  if (i != 1) pcl_panel[[i]] <- pcl_panel[[i]] + plot_layout(tag_level = "new")
}

fig3 <- wrap_elements(wrap_plots(pcl_panel, ncol = 3)) +
  p_expr +
  free(sank, type = "panel", side = "tbl") +
  free(
    p_gs_enr + theme(plot.title = element_text(hjust = 0.5)),
    type = "label",
    side = "tbr"
  ) +
  plot_layout(design = layout) +
  plot_annotation(tag_levels = "a") &
  theme(plot.tag = element_text(size = 18, face = "bold"))


ggsave(
  plot = fig3,
  filename = file.path(imgdir, "figure3_patchwork_panel.png"),
  height = 3600,
  width = 5000,
  units = "px"
)

ggsave(
  plot = fig3,
  filename = file.path(imgdir, "figure3_patchwork_panel.pdf"),
  height = 3600,
  width = 5000,
  device = cairo_pdf,
  units = "px"
)
```

```{r}
pcc_panel <- pc_corr_list
for (i in seq_len(length(pcc_panel))) {
  if (i != 1) pcc_panel[[i]] <- pcc_panel[[i]] + plot_layout(tag_level = "new")
}
pcc_panel <- wrap_plots(pcc_panel, ncol = 2, nrow = 3) +
  guide_area() +
  plot_layout(guides = "collect") &
  theme(
    legend.text = element_text(size = 14),
    legend.title = element_text(size = 16)
  )


layout <- c(
  area(1, 1, 4, 4),
  area(1, 5, 4, 8)
)
suppl_fig2 <-
  ((wrap_elements(pcc_panel)) +
    sank_anno) +
  plot_layout(width = c(2, 1), ncol = 2) +
  plot_annotation(tag_levels = "a") &
  theme(plot.tag = element_text(size = 18, face = "bold"))
# plot_layout(design = layout, ncol = 2)

ggsave(
  plot = suppl_fig2,
  filename = file.path(imgdir, "suppl_figure2_patchwork_panel.png"),
  height = 3600,
  width = 5000,
  units = "px"
)

ggsave(
  plot = suppl_fig2,
  filename = file.path(imgdir, "suppl_figure2_patchwork_panel.pdf"),
  height = 3600,
  width = 5000,
  device = cairo_pdf,
  units = "px"
)
```

# sessionInfo

```{r}
sessionInfo()
```
